### 2016-10-04 article/ms.tex
Init article, plot correlations between nodes

%% Copyright 2016 Andrew R. Casey.  All rights reserved.

\documentclass[preprint]{aastex}

\usepackage{amsmath}
\usepackage{bm}

\IfFileExists{vc.tex}{\input{vc.tex}}{\newcommand{\githash}{UNKNOWN}\newcommand{\giturl}{UNKNOWN}}

\newcommand{\acronym}[1]{{\small{#1}}}

\newcommand{\project}[1]{\textsl{#1}}

\newcommand{\teff}{T_{\mathrm{eff}}}
\newcommand{\logg}{\log g}
\newcommand{\feh}{[\mathrm{Fe/H}]}

\begin{document}
\title{The Gaia-ESO Survey: Combined estimates from multiple stellar analysis pipelines}

\author{
    Andrew~R.~Casey\altaffilmark{1}
}

\begin{abstract}
  Some stuff
\end{abstract}

\keywords{stars: fundamental parameters --- stars: abundances
% Clear rest of page
\clearpage}

\section{Introduction} 
\label{sec:introduction}

\section{Data}
\label{sec:data}

% Description of the setups

% Summary of the ges type and SNR of the data.

% Description of target sources included: MW, Clusters, CoRot, K2, etc.

% Blind test.

\section{Methods}
\label{sec:methods}

% Multiple analysis strategy: why

% primary advantage and disadvantage to multiple analysis strategy

% Description of two parameter rounds: stellar parameters, abundances

% What's reported by each node? Flags? Consistency of flags?

% Description of pipelines in appendix

% Commonalities between nodes: model atmospheres, line list, normalized spectra, initial params, spectrum library, xi calibration if necessary.

% EW method and comparisons -- into an appendix?.

% What do the nodes provide? Most parameters, flags, etc.

% CONTINUE from here:
% Stellar parameter determination

% Stellar parameter homogenisation

% Abundance determination

% Abundance homogenisation

\section{Discussion}
\label{sec:discussion}

% Is the multiple-analysis strategy justified?
% --> Take any one node, infer their uncertainties as a function of SNR using point-wise correlations (e.g., no benchmarks).
% --> What goes wrong for each node?

% Precision, accuracy, systematics.
% EW

% Analysis choices: we give same line list but not all are used.
%                   or how they are used.

\section{Conclusions}
\label{sec:conclusions}

% This should be a "lessons learned" list.

% The final paragraph should contain a succint forward outlook of how good or bad an idea this was.

\end{document}

### 2016-10-04 code/model/ensemble.py

@@ -550,9 +550,12 @@ class BaseEnsembleModel(object):
         return klass
 
 
-    def node_uncertainty_with_snr(self, **kwargs):
+    def plot_node_uncertainty_with_snr(self, **kwargs):
         return plot.node_uncertainty_with_snr(self, **kwargs)
 
+
+    def plot_node_correlations(self, **kwargs):
+        return plot.node_correlations(self, **kwargs)
 
 
 
@@ -902,6 +905,14 @@ class SingleParameterEnsembleModel(BaseEnsembleModel):
             "Sigma_c0": Sigma_c0,
             "Sigma_c1": Sigma_c1
         })
+
+        alpha_bounds = {
+            "teff": (100, 1000),
+            "logg": (0.1, 1),
+            "feh": (0.1, 1),
+        }
+        data_dict.update(
+            dict(zip(("lower_alpha", "upper_alpha"), alpha_bounds[parameter])))
 
         # Create additional metadata
         node_names = self._database.retrieve_table("SELECT * FROM nodes")

### 2016-10-04 code/model/plot.py

@@ -4,9 +4,13 @@ Plot things relevant to the ensemble model.
 """
 
 import cPickle as pickle
+import itertools
 import logging
 import numpy as np
+import scipy.sparse
+
 import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
 
 import brewer2mpl # For pretty colors.
 
@@ -15,7 +19,7 @@ logger = logging.getLogger("ges")
 _DEFAULT_SAVEFIG_KWDS = dict(dpi=300, bbox_inches="tight")
 
 def node_uncertainty_with_snr(model, quartiles=[2.5, 50, 97.5], N=1000,
-    show_wg_limit=True, xlims=(1, 500), ylims=(0, 500), hide_node_ids=None, 
+    show_wg_limit=True, xlims=(1, 500), ylims=None, hide_node_ids=None, 
     show_data_points=True, **kwargs):
     """
     Plot the total node uncertainty as a function of S/N ratio.
@@ -116,8 +120,6 @@ def node_uncertainty_with_snr(model, quartiles=[2.5, 50, 97.5], N=1000,
                 alpha=0.5, lw=2, facecolor="k")
             #ax.plot(bins[:-1] + 0.5 * np.diff(bins)[0], stds, c='k')
 
-
-
     if show_wg_limit:
         # Calculate the minimum variance as a function of SNR using all the
         # information from every node.
@@ -164,7 +166,6 @@ def node_uncertainty_with_snr(model, quartiles=[2.5, 50, 97.5], N=1000,
                 alpha=0.5, edgecolor="none", zorder=10)
 
     ax.set_xlim(*xlims)
-    ax.set_ylim(*ylims)
     ax.set_xlabel(r"${\rm Signal}$-${\rm to}$-${\rm noise}$ ${\rm ratio},$ $S/N$ $({\rm pixel}^{-1})$")
 
     default_ylabels = {
@@ -172,14 +173,20 @@ def node_uncertainty_with_snr(model, quartiles=[2.5, 50, 97.5], N=1000,
         "logg": r"${\rm Uncertainty}$ ${\rm in}$ ${\rm surface}$ ${\rm gravity},$ $\sigma_\log{g}$ $({\rm dex})$",
         "feh": r"${\rm Uncertainty}$ ${\rm in}$ ${\rm metallicity},$ $\sigma_{\rm [Fe/H]}$ $({\rm dex})$",
     }
[…]

### 2016-10-04 scripts/homogenise_all_wgs.py

@@ -51,65 +51,6 @@ for wg in wgs:
 
         if wg == 11 and parameter == "teff": continue
 
-        '''
-        model = SingleParameterEnsembleModel.read(model_path, database)
-        model._prepare_data()
-
-
-        # SHow heaps of shit.
-        data = database.retrieve_table(
-            """ SELECT DISTINCT ON (node_id, filename) r.id, node_id, nodes.name, spectra.ges_fld, teff, r.snr, TRIM(r.filename) as filename
-                FROM results as r, nodes, spectra
-                WHERE trim(spectra.ges_type) like 'GE_SD_B%'
-                  AND spectra.cname = r.cname
-                  AND r.node_id = nodes.id
-                  AND nodes.wg = '11'
-                  AND passed_quality_control
-                  AND teff <> 'NaN'
-            """)
-
-        data = data.group_by("node_id")
-
-        for group in data.groups:
-            fig, ax = plt.subplots()
-
-            diffs = []
-            keep = np.zeros(len(group), dtype=bool)
-            ges_flds = np.array([each.strip() for each in benchmarks["GES_FLD"]])
-            for i, row in enumerate(group):
-                match = ges_flds == row["ges_fld"].strip()
-                if any(match):
-                    diffs.append(row["teff"] - benchmarks["TEFF"][match])
-                    keep[i] = True
-
-            diffs = np.abs(diffs)
-
-
-
-            ax.scatter(group["snr"][keep], diffs, label=group["name"][0], alpha=0.5)
-
-            match = np.where(group["node_id"][0] == model._metadata["node_ids"])[0][0]
-
-            diffs = np.array([model._data["mu_calibrator"][index - 1]  for index in model._data["calibrator_index"]]) \
-                - model._data["estimates"][:, match]
-
-            ax.scatter(model._data["snr_spectrum"], np.abs(diffs), facecolor="r", alpha=0.5)
-
-
-
-
-
-            wtf = (diffs.flatten() > 1000) * (group["snr"][keep] > 100)
-
-            print(data[keep][wtf])
-
-            ax.set_title(group["name"][0])
-
-
-        raise a
-        '''
-
-
         if os.path.exists(model_path):
             model = SingleParameterEnsembleModel.read(model_path, database)
 
@@ -120,19 +61,26 @@ for wg in wgs:
             init = {
                 "truths": data["mu_calibrator"],
[…]

### 2016-10-04 code/model/plot.py
update gitignore and remove debugs

@@ -177,7 +177,7 @@ def node_uncertainty_with_snr(model, quartiles=[2.5, 50, 97.5], N=1000,
     ax.set_ylabel(ylabel)
 
     if ylims is None:
-        default_ylims = dict(teff=(0, 500), logg=(0, 0.5), feh=(0, 0.5))
+        default_ylims = dict(teff=(0, 500), logg=(0, 1), feh=(0, 0.5))
         ylims = default_ylims.get(model._parameter, None)
 
     ax.set_ylim(ylims)
@@ -338,5 +338,4 @@ def node_correlations(model, reorder=True, plot_edges=True,
     ])
     plt.show()
 
-    raise a
     return fig

### 2016-10-04 scripts/homogenise_all_wgs.py
dem bugz

@@ -27,7 +27,7 @@ database = GESDatabase(**credentials)
 # Only use "benchmarks" with TEFF < 8000 K
 benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
 benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
-benchmarks["E_FEH"] = 0.15
+benchmarks["E_FEH"] = 0.10
 
 model_paths = "homogenisation-wg{wg}-{parameter}.model"
 
@@ -48,8 +48,6 @@ for wg in wgs:
     for parameter, scale in parameter_scales.items():
 
         model_path = model_paths.format(wg=wg, parameter=parameter)
-
-        if wg == 11 and parameter == "teff": continue
 
         if os.path.exists(model_path):
             model = SingleParameterEnsembleModel.read(model_path, database)
@@ -78,7 +76,7 @@ for wg in wgs:
         fig.savefig("wg{}-{}-node-correlations.pdf".format(wg, parameter))
 
         fig = model.plot_node_uncertainty_with_snr(
-            show_data_points=False, legend_kwds=dict(ncols=2))
+            show_data_points=False, legend_kwds=dict(ncol=2))
         fig.savefig("wg{}-{}-node-uncertainties.pdf".format(wg, parameter))
 
         continue

### 2016-10-05 code/model/ensemble.py
use svd, etc

@@ -117,7 +117,7 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
         raise ValueError(
             "stan_model must be provided, or stan_chains and stan_data")
 
-    K = len(samples["var_intrinsic"])
+    K = samples["truths"].shape[0]
     M = len(set(estimates["node_id"]))
 
     if 1 > N or N > K:
@@ -155,8 +155,8 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
             mu = np.array(
                 estimates[parameter][s:e] + samples["c0_estimators"][i, k])
 
-            spectrum_snr = np.clip(estimates["snr"][s:e], 0.1, np.inf)
-            C = np.eye(L) * (samples["alpha_sq"][i, k]/spectrum_snr**2)
+            spectrum_snr = np.clip(estimates["snr"][s:e], 1, np.inf)
+            C = np.eye(L) * (samples["alpha"][i, k]**2/spectrum_snr)
 
             W = np.ones((L, 1))
             Cinv = np.linalg.inv(C)
@@ -180,15 +180,34 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
 
         # Gauss-Markov theorem.
         W = np.ones((M, 1))
-        Cinv = np.linalg.inv(C)
+
+        if np.linalg.cond(C) > np.finfo(matrix.dtype).eps:
+            # Matrix is ill-conditioned.
+            logger.warn("Covariance matrix is ill-conditioned.")
+
+            # Use SVD to invert matrix.
+            U, s, V = np.linalg.svd(C)
+            Cinv = np.dot(np.dot(V.T, np.linalg.inv(np.diag(s))), U.T)
+
+        else:
+            Cinv = np.linalg.inv(C)
+
         var = 1.0/np.dot(np.dot(W.T, Cinv), W)
-        mu = var * np.dot(np.dot(W.T, Cinv), mu_node)
+        if var < 0:
+            logger.warn("Negative variance returned!")
+            
+        mu = np.abs(var) * np.dot(np.dot(W.T, Cinv), mu_node)
 
         mu_samples[ii] = mu
         var_samples[ii] = var
 
-    central = np.median(mu_samples)
-    error = np.sqrt(np.median(var_samples))
+    central = np.nanmedian(mu_samples)
+    error = np.sqrt(np.nanmedian(np.abs(var_samples)))
+
+    if np.isfinite(central):
+        assert np.isfinite(error)
+
+    raise a
 
     if update_database:
[…]

### 2016-10-05 scripts/propagate_flags.py
Flag clearly erroneous results from WG11/IACAIP

@@ -39,6 +39,9 @@ database.update(
                 passed_quality_control = true
          WHERE  passed_quality_control = false;""")
 
+
+
+
 database.connection.commit()
 
 # Identify spurious spectra and mark them as such.
@@ -263,5 +266,25 @@ for key, value in qc_flags["node_specific_flags"].items():
             logger.info(
                 "Marked {} results as poor quality due to matching flag {} "\
                 "and constraint {}".format(N, flag, constraint))
+
+
+# Flag *CLEARLY* erroneous problems from the WG11/IACAIP node. Some of these will
+node_id = database.retrieve_node_id(11, "IACAIP")
+
+N = database.update(
+    """ UPDATE  results
+           SET  passed_quality_control = false,
+                propagated_tech = '10308-11-00-00-A'
+         WHERE  results.node_id = '{}'
+           AND  passed_quality_control
+           AND  (
+                    (teff <> 'NaN' AND (teff <= 3000 OR teff >= 8000))
+                    OR
+                    (logg <> 'NaN' AND (logg <= 0 OR logg >= 5))
+                    OR
+                    (feh <> 'NaN' AND (feh <= -3 OR feh >= 1))
+                );
+    """.format(node_id))
+logger.info("Marked {} WG11/IACAIP results as out-of-grid.")
 
 database.connection.commit()

### 2016-10-08 code/model/ensemble.py
Update model to account for systematic variance as a function of multiple stellar parameters

@@ -278,7 +278,12 @@ class BaseEnsembleModel(object):
         self._parameter = parameter
         self._calibrators = calibrators
 
-        self._model = self._load_model(recompile, overwrite, **kwargs)
+        model_code = kwargs.get("model_code", None)
+        if model_code is None:
+            self._model = self._load_model(recompile, overwrite, **kwargs)
+        else:
+            # We have model code -- use it.
+            raise a
 
         # For later.
         self._data = None
@@ -519,7 +524,8 @@ class BaseEnsembleModel(object):
                 "filename {} exists and not overwriting".format(filename))
 
         state = {
-            "model_path": self._MODEL_PATH, 
+            "model_path": self._MODEL_PATH,
+            "model_code": self._model.model_code, 
             "wg": self._wg,
             "parameter": self._parameter,
             "calibrators": self._calibrators,
@@ -562,7 +568,7 @@ class BaseEnsembleModel(object):
 
         klass = \
             cls(database, state["wg"], state["parameter"], state["calibrators"],
-                **kwargs)
+                model_code=state.get("model_code", None), **kwargs)
 
         # Update the klass.
         klass._data = state.get("data", None)
@@ -1137,14 +1143,18 @@ class MissingDataModel(BaseEnsembleModel):
             "visits": visits.astype(int),
 
             "is_missing": is_missing.astype(int),
-            "N_missing": np.sum(is_missing),
+            "TM": np.sum(is_missing),
 
             "estimates": estimates,
             "spectrum_ivar": spectrum_ivar.T,
             "spectrum_isnr": 1.0/np.sqrt(spectrum_ivar.T),
 
             "mu_calibrator": mu_calibrator,
-            "sigma_calibrator": sigma_calibrator
+            "sigma_calibrator": sigma_calibrator,
+
+            "S": 3, # TODO: Make this flexible? Make the calibrator values accessible from kwargs?
+            "all_mu_calibrator": np.vstack(
+                [calibrators[p] for p in ("TEFF", "LOGG", "FEH")]).T
         }
 
         alpha_bounds = dict(teff=(100, 1000), logg=(0.1, 1.0), feh=(0.1, 1.0))

### 2016-10-08 code/model/plot.py

@@ -18,6 +18,102 @@ logger = logging.getLogger("ges")
 
 _DEFAULT_SAVEFIG_KWDS = dict(dpi=300, bbox_inches="tight")
 
+
+def node_systematic_uncertainty(model, quartiles=[2.5, 50, 97.5], N=1000,
+    ylims=None, hide_node_ids=None):
+    """
+    Plot the systematic uncertainty from all nodes as a function of the stellar
+    parameters.
+    """
+
+    quartiles = np.hstack(quartiles)
+    Q = len(quartiles)
+    if Q not in (1, 3):
+        raise ValueError("quartiles must be length 1 or 3")
+
+    chains = model._chains
+    assert chains is not None, "Has the model been sampled?"
+
+    xN = 500 
+
+    # Get sample indices.
+    K = chains["truths"].shape[0]
+    N = K if not K >= N > 0 else N
+    indices = np.random.choice(range(K), N, replace=False)
+
+    node_ids = model._data["node_ids"]
+    hide_node_ids = hide_node_ids or []
+
+    L = len(node_ids)
+    colors = brewer2mpl.get_map("Set1", "qualitative", L).mpl_colors[::-1]
+    parameters = ("teff", "logg", "feh")
+
+    parameter_ranges = {
+        "teff": (3000, 8000),
+        "logg": (0, 5),
+        "feh": (-3, 0.5)
+    }
+
+    fig, axes = plt.subplots(3)
+
+    x_all = np.array([np.linspace(*(list(parameter_ranges[parameter]) + [xN])) \
+        for parameter in parameters])
+
+    # Design matrix.
+    M = np.ones((7, xN))
+    M[1] = (x_all[0] - parameter_ranges["teff"][0])/np.ptp(parameter_ranges["teff"])
+    M[2] = (x_all[1] - parameter_ranges["logg"][0])/np.ptp(parameter_ranges["logg"])
+    M[3] = (x_all[2] - parameter_ranges["feh"][0])/np.ptp(parameter_ranges["feh"])
+    M[4] = M[1]**2
+    M[5] = M[2]**2
+    M[6] = M[3]**2
+
+    for j, (ax, parameter) in enumerate(zip(axes, parameters)):
+
+        x = x_all[j]
+        x_scaled = (x_all[j] - parameter_ranges[parameter][0])/np.ptp(parameter_ranges[parameter])
+
+        for i, node_id in enumerate(set(node_ids).difference(hide_node_ids)): 
+            
+            k = np.where(node_id == node_ids)[0][0]
+
[…]

### 2016-10-08 scripts/homogenise_fast.py

@@ -38,7 +38,7 @@ parameter_scales = OrderedDict([
     ("feh", 0.25)
 ])
 
-sample_kwds = dict(chains=4, iter=2000)
+sample_kwds = dict(chains=4, iter=10000, thin=10)
 
 finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
 benchmarks = benchmarks[finite]
@@ -49,37 +49,45 @@ for wg in wgs:
     for parameter, scale in parameter_scales.items():
 
         model_path = model_paths.format(wg=wg, parameter=parameter)
+        if os.path.exists(model_path): continue
+
 
         model = MissingDataModel(database, wg, parameter, benchmarks)
         data, metadata = model._prepare_data(
             default_sigma_calibrator=scale)
-        
+
 
         init = {
             "truths": data["mu_calibrator"],
             "biases": np.zeros(data["N"]),
-            "missing_estimates": np.mean([data["upper_bound"], data["lower_bound"]]) * np.ones(data["N_missing"]),
-            "alpha_sq": 500**2 * np.ones(data["N"]),
-            "variance_sys": scale**2 * np.ones(data["N"]),
+            "missing_estimates": np.random.uniform(
+                data["lower_bound"], data["upper_bound"], size=data["TM"]),
+            "alpha_sq": np.mean([data["lower_alpha_sq"], data["upper_alpha_sq"]]) * np.ones(data["N"]),
+            "vs_c": scale**2 * np.ones(data["N"]),
+            "vs_a": 1e-2 + np.zeros((data["N"], data["S"])).T,
+            "vs_b": 1e-2 + np.ones((data["N"], data["S"])).T,
             "L_corr": np.eye(data["N"])
         }
 
-        raise a
+        print("Number of model parameters: {}".format(
+            sum([np.array(v).size for v in init.values()])))
+
         op_params = model.optimize(data, init=init, iter=100000)
 
-        raise a
         fit = model.sample(data, init=op_params, **sample_kwds)
 
-        model.write(model_path, overwrite=True)
+        model.write(model_path, 
+            overwrite=True, __ignore_model_pars=("Sigma", "full_rank_estimates"))
+
 
         # Keep the model.
         models[wg][parameter] = model
 
+        continue
+
 
         # Plot some stuff.
         fig = model.plot_node_correlations()
-        
-        raise a
[…]

### 2016-10-10 code/model/ensemble.py
Cleaning up and plotting more

@@ -280,11 +280,11 @@ class BaseEnsembleModel(object):
 
         model_code = kwargs.get("model_code", None)
         if model_code is None:
-            self._model = self._load_model(recompile, overwrite, **kwargs)
-        else:
-            # We have model code -- use it.
-            raise a
+            with open(self._MODEL_PATH, "r") as fp:
+                model_code = fp.read()
 
+        self._model_code = model_code
+        
         # For later.
         self._data = None
         self._fit = None
@@ -587,388 +587,11 @@ class BaseEnsembleModel(object):
 
 
 
-class MeanEnsembleModel(BaseEnsembleModel):
+class EnsembleModel(BaseEnsembleModel):
 
     _MODEL_PATH = os.path.join(
         os.path.dirname(os.path.realpath(__file__)),
-        "mean-ensemble-model-with-correlations.stan")
-
-    def _prepare_data(self, parameter=None, default_sigma_calibrator=1e3,
-        fill_function=np.mean, fill_variance=1e50, require_no_gaps=False,
-        maximum_snr=500, 
-        sql_constraint=None):
-        """
-        Prepare the data for the model so that it can be supplied to Stan.
-
-        """        
-        parameter = str(parameter or self._parameter).lower()
-        if parameter not in ("teff", "logg", "feh", "xi", "mh"):
-            raise AreYouSureYouKnowWhatYoureDoing
-
-        # Get the data from the database for this WG.
-        # TODO: Need a better way to identify calibrators. Right now we do it
-        #       just on GES_TYPE, but in future we may want to do this directly
-        #       on to CNAMEs in the calibrator list.
-        data = self._database.retrieve_table(
-            """ WITH    n AS (
-                            SELECT id FROM nodes WHERE wg = {wg}), 
-                        s AS (
-                            SELECT cname, ges_type, ges_fld
-                            FROM spectra
-                            WHERE ges_type LIKE 'GE_SD_B%') 
-                SELECT DISTINCT ON (r.filename, r.node_id) 
-                    s.cname, s.ges_type, s.ges_fld,
-                    r.filename, r.node_id, r.snr,
-                    r.{parameter}, r.e_{parameter}
-                FROM    s, n, results as r 
-                WHERE r.cname = s.cname 
-                  AND r.node_id = n.id 
-                  AND r.{parameter} <> 'NaN'
-                  AND r.passed_quality_control
-                      {sql_constraint}
-                """.format(
-                    wg=self._wg, parameter=parameter,
[…]

### 2016-10-10 code/model/plot.py

@@ -19,8 +19,8 @@ logger = logging.getLogger("ges")
 _DEFAULT_SAVEFIG_KWDS = dict(dpi=300, bbox_inches="tight")
 
 
-def node_systematic_uncertainty(model, quartiles=[2.5, 50, 97.5], N=1000,
-    ylims=None, hide_node_ids=None):
+def node_systematic_uncertainty(model, axes=None, quartiles=[16, 50, 84], Ns=100, 
+    ylims=None):
     """
     Plot the systematic uncertainty from all nodes as a function of the stellar
     parameters.
@@ -34,89 +34,62 @@ def node_systematic_uncertainty(model, quartiles=[2.5, 50, 97.5], N=1000,
     chains = model._chains
     assert chains is not None, "Has the model been sampled?"
 
-    xN = 500 
+    nodes = (model._metadata["node_ids"], model._metadata["node_names"])
 
-    # Get sample indices.
-    K = chains["truths"].shape[0]
-    N = K if not K >= N > 0 else N
-    indices = np.random.choice(range(K), N, replace=False)
+    N = len(nodes[0])
+    colors = brewer2mpl.get_map("Set1", "qualitative", N + 1).mpl_colors
 
-    node_ids = model._data["node_ids"]
-    hide_node_ids = hide_node_ids or []
+    if axes is None:
+        fig, axes = plt.subplots(1, 3)
+    else:
+        fig = axes[0].figure
 
-    L = len(node_ids)
-    colors = brewer2mpl.get_map("Set1", "qualitative", L).mpl_colors[::-1]
+    # MAGIC HACK TODO
     parameters = ("teff", "logg", "feh")
+    bounds = [
+        (3000, 8000),
+        (0, 5),
+        (-3.5, 0.5)
+    ]
 
-    parameter_ranges = {
-        "teff": (3000, 8000),
-        "logg": (0, 5),
-        "feh": (-3, 0.5)
-    }
+    if ylims is None:
+        ylims = dict(teff=(0, 500), logg=(0, 0.5), feh=(0, 0.5))
 
-    fig, axes = plt.subplots(3)
+    K = len(parameters)
+    S = 500
+    xs = np.linspace(0, 1, S)
 
-    x_all = np.array([np.linspace(*(list(parameter_ranges[parameter]) + [xN])) \
-        for parameter in parameters])
+    for i, (ax, bound) in enumerate(zip(axes, bounds)):
 
[…]

### 2016-10-10 sandbox_plot.py
add sandbox plotting script

@@ -1,0 +1,14 @@
+
+import matplotlib.pyplot as plt
+
+from code.model import ensemble, plot
+
+
+model = ensemble.EnsembleModel.read("homogenisation-wg11-teff.model", None)
+
+
+#plot.biases(model)
+
+#plot.node_uncertainty_with_snr(model)
+
+plot.node_systematic_uncertainty(model)

### 2016-10-10 code/model/ensemble.py
Update some bits

@@ -9,7 +9,9 @@ import numpy as np
 import os
 import pystan as stan
 from astropy.table import Table
+from collections import OrderedDict
 from itertools import combinations
+from time import time
 
 from . import plot
 
@@ -41,7 +43,7 @@ def _guess_parameter_names(table, names):
 
 
 def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
-    stan_model=None, stan_chains=None, stan_data=None, update_database=True):
+    stan_model=None, update_database=True):
     """
     Produce an unbiased estimate of an astrophyiscal parameter for a given
     survey object.
@@ -64,25 +66,13 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
 
         Either the fitted stan model must be provided, or the Stan chains and 
         the data dictionary (`stan_chains` and `stan_data`) must be provided.
-
-    :param stan_chains: [optional]
-        The extracted samples (chains) from the sampled Stan model.
-
-        Either the `stan_model` must be provided, or the Stan chains and
-        the data dictionary (`stan_chains` and `stan_data`) must be provided.
-
-    :param stan_data: [optional]
-        The data dictionary provided to Stan.
-
-        Either the `stan_model` must be provided, or the Stan chains and
-        the data dictionary (`stan_chains` and `stan_data`) must be provided.    
     """
 
     # Get the data for this object.
     estimates = database.retrieve_table(
         """ SELECT  DISTINCT ON (filename, node_id)
                     results.id, cname, node_id, snr, trim(filename) as filename, 
-                    {parameter}
+                    teff, logg, feh
             FROM    results, nodes
             WHERE   nodes.wg = {wg}
               AND   nodes.id = results.node_id
@@ -92,7 +82,7 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
         """.format(wg=wg, cname=cname, parameter=parameter))
 
     if estimates is None:
-        return (np.array([np.nan]), np.array([np.nan]))
+        return np.nan * np.ones(4)
 
     # Extract N samples for all the parameters.
 
@@ -105,17 +95,8 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
     #   4. Draw from a Gaussian using the weighted means and your new Cov matrix
[…]

### 2016-10-10 code/model/plot.py

@@ -10,6 +10,7 @@ import numpy as np
 import scipy.sparse
 
 import matplotlib.pyplot as plt
+from collections import OrderedDict
 from matplotlib.ticker import MaxNLocator
 
 import brewer2mpl # For pretty colors.
@@ -19,8 +20,78 @@ logger = logging.getLogger("ges")
 _DEFAULT_SAVEFIG_KWDS = dict(dpi=300, bbox_inches="tight")
 
 
-def node_systematic_uncertainty(model, axes=None, quartiles=[16, 50, 84], Ns=100, 
-    ylims=None):
+def systematic_uncertainty(model, ax=None, N_bins=50, xlabel=None, legend=True,
+    **kwargs):
+    """
+    Plot the distribution of constant systematic uncertainties from all nodes.
+
+    :param model:
+        A fully-sampled ensemble model.
+
+    """
+
+    if ax is None:
+        fig, ax = plt.subplots()
+    else:
+        fig, ax = ax.figure, ax
+
+    N = model._chains["vs_c"].shape[1]
+
+    colors = brewer2mpl.get_map("Set1", "qualitative", N).mpl_colors
+
+    max_abs_sigma = np.sqrt(np.max(np.abs(model._chains["vs_c"])))
+    bins = np.linspace(0, max_abs_sigma, N_bins)
+
+    nodes = (model._metadata["node_ids"], model._metadata["node_names"])
+    for i, (node_id, node_name) in enumerate(zip(*nodes)):
+
+        ax.hist(np.sqrt(model._chains["vs_c"][:, i]),
+            facecolor=colors[i], edgecolor=colors[i], bins=bins, 
+            alpha=0.5, lw=2, normed=True, histtype="stepfilled",
+            label=r"${{\rm {0}}}$".format(node_name.strip()))
+
+    latex_labels = {
+        "teff": r"${\rm Constant}$ ${\rm systematic}$ ${\rm uncertainty}$ "
+                r"${\rm in}$ ${\rm effective}$ ${\rm temperature},$ "
+                r"$\sigma_{c,T_{\rm eff}}$ $({\rm K})$",
+        "logg": r"${\rm Constant}$ ${\rm systematic}$ ${\rm uncertainty}$ "
+                r"${\rm in}$ ${\rm surface}$ ${\rm gravity},$ "
+                r"$\sigma_{c,\log{g}}$ $({\rm dex})$",
[…]

### 2016-10-10 sandbox_plot.py

@@ -1,14 +1,47 @@
 
-import matplotlib.pyplot as plt
 
 from code.model import ensemble, plot
 
 
-model = ensemble.EnsembleModel.read("homogenisation-wg11-teff.model", None)
+for wg in (11, ):
 
+    for parameter in ("teff", "logg", "feh"):
 
-#plot.biases(model)
+        model = ensemble.EnsembleModel.read(
+            "homogenisation-wg11-{}.model".format(parameter), None)
 
-#plot.node_uncertainty_with_snr(model)
+        # Plot the distribution of biases for each node
+        fig = plot.biases(model)
+        fig.savefig("figures/wg{wg}/wg{wg}-biases-{param}.pdf".format(
+            wg=wg, param=parameter))
+        fig.savefig("figures/wg{wg}/wg{wg}-biases-{param}.png".format(
+            wg=wg, param=parameter))
+        
 
-plot.node_systematic_uncertainty(model)
+        # Plot the random uncertainty as a function of SNR
+        fig = plot.node_uncertainty_with_snr(model)
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-random-{param}.pdf"\
+            .format(wg=wg, param=parameter))
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-random-{param}.png"\
+            .format(wg=wg, param=parameter))
+
+        # Plot the relative systematic uncertainty as a function of parameters
+        fig = plot.node_relative_systematic_uncertainty(model)
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-sys-relative-{param}.pdf"\
+            .format(wg=wg, param=parameter))
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-sys-relative-{param}.png"\
+            .format(wg=wg, param=parameter))
+
+        # Plot the baseline systematic uncertainty
+        fig = plot.systematic_uncertainty(model)
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-sys-constant-{param}.pdf"\
+            .format(wg=wg, param=parameter))
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-sys-constant-{param}.png"\
+            .format(wg=wg, param=parameter))
+
+        # Plot node correlations.
+        fig = plot.node_correlations(model)
[…]

### 2016-10-10 scripts/homogenise_fast.py

@@ -12,7 +12,7 @@ from collections import OrderedDict
 
 
 from code import GESDatabase
-from code.model.ensemble import MissingDataModel
+from code.model.ensemble import EnsembleModel
 
 # Initialize logging.
 logger = logging.getLogger("ges")
@@ -49,59 +49,38 @@ for wg in wgs:
     for parameter, scale in parameter_scales.items():
 
         model_path = model_paths.format(wg=wg, parameter=parameter)
-        if os.path.exists(model_path): continue
+        if os.path.exists(model_path): 
+            model = EnsembleModel.read(model_path, database)
+
+        else:
+            model = EnsembleModel(database, wg, parameter, benchmarks)
+            data, metadata = model._prepare_data(
+                default_sigma_calibrator=scale)
+
+            init = {
+                "truths": data["mu_calibrator"],
+                "biases": np.zeros(data["N"]),
+                "missing_estimates": np.random.uniform(
+                    data["lower_bound"], data["upper_bound"], size=data["TM"]),
+                "alpha_sq": np.mean([data["lower_alpha_sq"], data["upper_alpha_sq"]]) * np.ones(data["N"]),
+                "vs_c": scale**2 * np.ones(data["N"]),
+                "vs_a": 1e-2 + np.zeros((data["N"], data["S"])).T,
+                "vs_b": 1e-2 + np.ones((data["N"], data["S"])).T,
+                "L_corr": np.eye(data["N"])
+            }
+
+            print("Number of model parameters: {}".format(
+                sum([np.array(v).size for v in init.values()])))
+
+            op_params = model.optimize(data, init=init, iter=100000)
+
+            fit = model.sample(data, init=op_params, **sample_kwds)
+
+            model.write(model_path, 
+                overwrite=True, __ignore_model_pars=("Sigma", "full_rank_estimates"))
 
 
-        model = MissingDataModel(database, wg, parameter, benchmarks)
-        data, metadata = model._prepare_data(
-            default_sigma_calibrator=scale)
-
-
-        init = {
-            "truths": data["mu_calibrator"],
-            "biases": np.zeros(data["N"]),
-            "missing_estimates": np.random.uniform(
-                data["lower_bound"], data["upper_bound"], size=data["TM"]),
-            "alpha_sq": np.mean([data["lower_alpha_sq"], data["upper_alpha_sq"]]) * np.ones(data["N"]),
[…]

### 2016-10-10 article/ms.tex
Some words

@@
 
+\newcommand{\ges}{\acronym{GES}}
 \newcommand{\project}[1]{\textsl{#1}}
+
+\newcommand{\gaiaeso}{\project{Gaia-ESO}}
 
@@
 \newcommand{\feh}{[\mathrm{Fe/H}]}
+\newcommand{\normal}[2]{\mathcal{N}\left(#1, #2\right)}
 
@@
 \author{
-    Andrew~R.~Casey\altaffilmark{1}
+    Andrew~R.~Casey\altaffilmark{1},
    }
@@
 \label{sec:introduction}
+
+% In terms of telescope time cost, GES is the largest by far.
+
+% Huge time allocation to do heaps of cool shit.
+
+% Analyse all spectral types
+
+% Provides a ground-based complement to the Gaia mission.
+
+% Huge collaboration, most of which were in-fighting previously.
+
+% Through GES they started working together....
+
+% Experts in different fields, etc.
+
+% Multiple analysis strategy.
 
@@
 % Stellar parameter homogenisation
+\subsection{Stellar parameter homogenisation}
+\label{sec:stellar-parameter-homogenisation}
+
+Flag propagation.
+
+\noindent{}We make the following assumptions when constructing a model for homogenisation:
+
+\begin{itemize}
+    \item   \emph{The uncertainties reported by each node are incorrect.}
+            This assumption is based on a cursory examination of the data:
+            some nodes do not provide uncertainties in stellar parameters, and
+            the uncertainties reported by some nodes could vary in percent by
+            two orders of magnitude. Therefore, we assume that each node only
+            provides a point estimate for astrophysical parameters.
+
+    \item   \emph{Every node provides a biased estimate of stellar parameters.}
+            We assume that every node has an unknown bias $\beta$ (offset) in each
+            astrophysical parameter,
+
+            \begin{eqnarray}
+                \mu_{true} = \mu_{node} + \beta_{node} + \epsilon
+            \end{eqnarray}
+
+            \noindent{}where $\epsilon$ represents the noise in the estimate.
+
+    \item   \emph{The unbiased stellar parameters from any two nodes are correlated.}
+            After accounting for individual node biases, we assume that the 
+            stellar parameters reported by any two nodes will be correlated
+            to some degree. The level of correlation between two nodes is unknown.
+            This assumption arises from commonalities that led to the estimates from
+            each node. Specifically: all nodes are instructed to use a common list 
+            of line transitions, the same MARCS model photospheres, some nodes employ
+            similar methods (e.g., spectral synthesis), and all nodes derive their 
+            estimates from the same data (in some instances, even the same 
+            continuum-normalized spectra are used).
+
+            We note that even two nodes with identical methods are not guaranteed
+            to be perfectly correlated, because the \emph{choice} of which transitions
+            or spectral regions to use is not prescribed.
+
+    \item   \emph{There are gaps in the data.} 
+            No spectrum is guaranteed to have stellar parameters reported by all
+            nodes. This assumption is a consequence of the different expertise in
+            \gaiaeso: no node or method is expert across the entire range of parameter
+            space explored. If stellar parameters are not reported, then the reason 
+            must be specified through a \texttt{TECH} flag (see Section \ref{sec:flags}
+            on flag usage).
+
+    \item   \emph{Random uncertainties in stellar parameters will increase with
+            decreasing S/N ratio.}
+
+    \item   \emph{All `well-studied' stars have noisy measurement, and their values
+            are not known with infinite precision.} But we assume they are unbiased!
+
+    \item   \emph{The systematic uncertainty will vary across parameter space.}
+
+    \item   \emph{All stellar parameter estimates are normally-distributed draws about 
+            the true astrophysical value.}
+
+    \item   \emph{The effective temperature $\teff$, surface gravity $\logg$, and
+            metallicity $\feh$ for a single star are uncorrelated.}
+            This assumption is provably incorrect, and is made for practical reasons
+            only. In Section \ref{sec:scaling-the-model} we describe how the number
+            of model parameters scales, and in Section \ref{sec:model-parameterisation}
+            we explain how the inference problem itself is numerically unstable.
+            Including correlations in stellar parameters would require a constant
+            correlation term $\rho$, or modeling $\rho$ as a function of the stellar
+            parameters. In either case, the number of model parameters that require
+            MCMC will immediately increase by at least factor of three (e.g.,
+            $\gtrsim5{,}000$ parameters), amplifying numerical stability issues and
+            substantially increasing the requisite number of MCMC samples. For these
+            reasons, simultaneously modeling the correlation between stellar
+            parameters has been left for an extension of this work.
+
+\end{itemize}
+
+Given these assumptions the model we adopt is
+\begin{eqnarray}
+    \mu_{bm} = \normal{\mu_{true}}{\sigma_{bm}} 
+\end{eqnarray}
+
+% List of the model parameters
+
+We list the nomenclature and descriptions for all model parameters in Table 
+\ref{tab:model-parameters}. The number of total model parameters is given by
+\begin{eqnarray}
+    N_{parameters} = N_{calibrators} + N_{missing} + 6N_{nodes} + \frac{N_{nodes}!}{2(N_{nodes} - 2)!}
+\end{eqnarray}
+where $N_{calibrators}$ accounts for the true values of the calibrators, the
+$N_{missing}$ models the missing data points for the calibrator spectra, the
+$6N_{nodes}$ summarises parameters that model biases, as well as systematic
+and random uncertainties. The final term $\frac{N_{nodes}!}{2(N_{nodes} - 2)!}$
+is the number of correlation coefficients between all nodes.\footnote{In practice
+we include the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $\rho$
+as model parameters instead of directly modeling the $\rho$ terms.  The correlation
+matrix can be reconstructed by $\rho = (IL)\cdot(IL)^T$ where $I$ is the $N \times N$
+identity matrix. This parameterisation helps ensure that the resulting covariance
+matrix $\mathbf{\Sigma}$ is positive semi-definite, and can therefore be used for
+sampling.}
+
+% Priors
+
+% How does the model scale?
+
+% The implementation details.
+% Inheritly unstable
+% Cholesky decomposition
 

### 2016-10-11 article/ms.tex
sum shit

@@
 and random uncertainties. The final term $\frac{N_{nodes}!}{2(N_{nodes} - 2)!}$
-is the number of correlation coefficients between all nodes.\footnote{In practice
+is the number of correlation coefficients between all nodes.\footnote{
+This inference problem is numerically unstable, as there are many model parameters
+which are used toi
+
+ construct a covariance matrix that is sampled
+
+In practice
 we include the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $\rho$
@@
 
-% How does the model scale?
+We implemented the model in \texttt{Stan}, a probabilistic programming
+language, and the code describing our parameterisation is included as Appendix \ref{
+appendix:stan-code}. We initialised the model with $\mu_{true}$ at the central
+calibrator values, and set XXXXXX, with no correlation between any nodes. We
+optimized all parameters in \texttt{Stan} using the Broyden-Fletcher-Goldfarb-Shanno
+algorithm. The optimized point was used as an initialisation point for Markov Chain
+Monte-Carlo (MCMC) sampling.
 
-% The implementation details.
-% Inheritly unstable
-% Cholesky decomposition
+N chains, thinning, N iterations. Convergence criteria.
 

### 2016-10-11 code/model/ensemble.py
Ship WG11 products and figures

@@ -259,7 +259,127 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
 
 
 
+class MedianModel(object):
 
+    def __init__(self, database, wg, parameter, default_sigma=None, **kwargs):
+        self._database = database
+        self._wg = wg
+        self._parameter = parameter
+        if default_sigma is None:
+            self._default_sigma = {
+                "xi": 0.5,
+                "alpha_fe": 0.5,
+            }.get(parameter)
+        
+        else:
+            self._default_sigma = default_sigma
+
+        return None
+
+
+    def _homogenise_survey_measurement(self, cname, update_database=False,
+        **kwargs):
+
+        param = self._parameter
+
+        # Just return a median and stddev.
+        records = self._database.retrieve_table(
+            """ SELECT results.id, node_id, filename, {parameter}, e_{parameter}
+                  FROM results, nodes
+                 WHERE results.node_id = nodes.id
+                   AND nodes.wg = '{wg}'
+                   AND results.cname = '{cname}'
+                   AND results.passed_quality_control;""".format(
+                    parameter=param, wg=self._wg, cname=cname))
+
+        if records is None:
+            return {}
+
+        N = len(set(records["node_id"]))
+        S = len(set(records["filename"]))
+        mu = np.nanmedian(records[param])
+        sigma = np.nanstd(records[param])/np.sqrt(S)
+        provenance = list(records["id"].data.astype(int))
+
+        if np.isfinite(mu) and (not np.isfinite(sigma) or sigma <= 0):
+            sigma = kwargs.get("default_sigma", self._default_sigma)
+
+        result = {
+            "wg": self._wg, 
+            "cname": cname, 
+            param: mu, 
+            "e_{}".format(param): sigma,
+            "nn_nodes_{}".format(param): N,
+            "nn_spectra_{}".format(param): S,
+            "provenance_ids_for_{}".format(param): provenance
+        }
+
+        logger.info(
+            "Homogenised {} for {}/{}: {:.2f} +/- {:.2f} ({} spectra; {} nodes)"\
+            .format(param, self._wg, cname, mu, sigma, S, N))
+
+        if update_database:
+
+            record = self._database.retrieve(
+                """ SELECT id
+                      FROM wg_recommended_results
+                     WHERE wg = %s
+                       AND cname = %s
+                """, (self._wg, cname, ))
+
+            if record:
+                self._database.update(
+                    """ UPDATE wg_recommended_results
+                           SET {}
+                         WHERE id = '{}'""".format(
[…]

### 2016-10-11 code/plot/benchmarks.py

@@ -1,6 +1,6 @@
 
 
-
+import logging
 import numpy as np
 import os
 import matplotlib.pyplot as plt
@@ -10,10 +10,11 @@ from matplotlib import gridspec
 
 import utils
 
-__all__ = ["node_benchmark_performance"]
+__all__ = ["node_benchmark_performance", "wg_benchmark_performance"]
 
 benchmark_filename = "fits-templates/benchmarks/GES_iDR5_FGKMCoolWarm_Benchmarks_AcceptedParams_01082016.fits"
 
+logger = logging.getLogger("ges")
 
 def node_benchmark_performance(database, wg, node_name, sort_by="TEFF",
     ylims=None):
@@ -95,6 +96,9 @@ def node_benchmark_performance(database, wg, node_name, sort_by="TEFF",
         # Show box-and-whisker plot.
         N += np.hstack(diff).size
         bp = ax.boxplot(diff, widths=width, patch_artist=True)
+        ax.set_xlim(-0.5, len(benchmarks) + 0.5)
+        raise CHECKTHIS
+
         ax.set_ylabel(ylabels.get(parameter))
         ylim = ylims.get(parameter, None)
         if ylim is not None:
@@ -138,6 +142,243 @@ def node_benchmark_performance(database, wg, node_name, sort_by="TEFF",
         plt.setp(bp["whiskers"], color="k", linestyle="solid", linewidth=0.5)
         plt.setp(bp["boxes"], color="k", alpha=0.5, linewidth=1)
 
+    fig.tight_layout()
+    
+    return fig if N > 0 else None
+
+
+
+def wg_benchmark_performance(database, wg, truths, show_recommended=False,
+    sort_by=None, ylims=None, node_sql_constraint=None, skip_missing=True,
+    show_num_estimates=None, xlabels=None, ylabels=None, **kwargs):
+    """
+    Show a box-and-whisker plot for the benchmark parameters reported by a given
+    node.
+
+    :param database:
+        A database for transactions.
+
+    :param wg:
+        The working group.
+
+    :param truths:
+        An :astropy.table.Table: with the accepted "truth" values for the
+        benchmark stars. A `GES_FLD` column is required for matching.
+
+    :param show_recommended: [optional]
+        Show the recommended values from the working group.
+
+    :param sort_by: [optional]
+        A column in the `truths` table to sort the benchmarks by.
+
+    :param ylims: [optional]
+        A dictionary containing the absolute y-limit for each label (teff, logg,
[…]

### 2016-10-11 code/plot/cluster.py

@@ -103,7 +103,7 @@ def param_vs_param(database, wg, node_name, ges_fld, reference_parameter,
 
 
 
-def cluster(database, wg, node_name, ges_fld, vel_range=None,
+def cluster(database, ges_fld, wg, node_name=None, vel_range=None,
     isochrone_filename=None, limit_to_isochrone_range=False, ax=None,
     no_tech_flags=False, show_legend=True, **kwargs):
     """
@@ -113,11 +113,15 @@ def cluster(database, wg, node_name, ges_fld, vel_range=None,
     :param database:
         A database for transactions.
 
+    :param ges_fld:
+        The `GES_FLD` entry for the cluster.
+
     :param wg:
         The working group.
 
-    :param node_name:
-        The name of the node to show results for.
+    :param node_name: [optional]
+        The name of the node to show results for. If `None` is provided, then
+        recommended results will be shown for the specified working group `wg`.
 
     :param ges_fld:
         The name of the cluster (as listed in GES_FLD).
@@ -143,9 +147,16 @@ def cluster(database, wg, node_name, ges_fld, vel_range=None,
     vmin = kwargs.pop("vmin", None)
     vmax = kwargs.pop("vmax", None)
 
+    if node_name is not None:
+        # Get the data.
+        table = "results"
+        node_id = database.retrieve_node_id(wg, node_name)
+        sql_constraint = "AND r.node_id = '{}'".format(node_id)
 
-    # Get the data.
-    node_id = database.retrieve_node_id(wg, node_name)
+    else:
+        table = "wg_recommended_results"
+        sql_constraint = "AND r.wg = '{}'".format(wg)
+
     
     if no_tech_flags:
         tech_flag_constraint = " AND TRIM(r.TECH) = ''"
@@ -156,20 +167,22 @@ def cluster(database, wg, node_name, ges_fld, vel_range=None,
     # Collect the results for this node.
     results = database.retrieve_table(
         """ SELECT  DISTINCT ON (r.cname)
-                    r.cname, r.node_id, r.setup, s.filename, s.vel, s.e_vel, 
+                    r.cname, s.vel, s.e_vel, 
                     r.teff, r.e_teff, r.logg, r.e_logg, r.feh, r.e_feh, r.mh, r.e_mh
-            FROM    results r, spectra s 
+            FROM    {table} r, spectra s 
             WHERE   r.cname = s.cname
-                AND TRIM(s.ges_fld) = %s
[…]

### 2016-10-11 code/plot/utils.py

@@ -44,6 +44,10 @@ def wg_as_int(wg):
 
 def mh_or_feh(table):
 
+    if table["mh"][0] is None:
+        return "feh"
+    elif table["feh"][0] is None:
+        return "mh"
     feh = np.sum(np.isfinite(table["feh"]))
     mh = np.sum(np.isfinite(table["mh"]))
 

### 2016-10-11 code/ship.py

@@ -1,0 +1,180 @@
+
+""" Fucking :shipit: """
+
+import logging
+import numpy as np
+from astropy.io import fits
+from astropy.table import Table
+from datetime import datetime
+
+import utils
+from db import Database
+
+logger = logging.getLogger("ges")
+
+
+def wg_recommended_sp_template(database, input_path, output_path, wg,
+    ext=-1, overwrite=False, **kwargs):
+    """
+    Produce a WG-recommended file of stellar parameters from the template 
+    provided (on a per CNAME) basis.
+
+    :param database:
+        A database to connect to.
+
+    :param input_path:
+        The local file path of the WG-recommended template file.
+
+    :param output_path:
+        The local file path where to save the WG-recommended file to.
+
+    :param wg:
+        The working group.
+
+    :param ext: [optional]
+        The extension of the template to use for updating.
+
+    :param overwrite: [optional]
+        Overwrite the `output_path` if it already exists.
+    """
+
+    columns = [
+        "teff",
+        "e_teff",
+        "e_pos_teff",
+        "e_neg_teff",
+        "nn_nodes_teff",
+        "nn_spectra_teff",
+        "enn_teff",
+        "nne_teff",
+        "sys_err_teff",
+        
+        "logg",
+        "e_logg",
+        "e_pos_logg",
+        "e_neg_logg",
+        "nn_nodes_logg",
+        "nn_spectra_logg",
+        "enn_logg",
+        "nne_logg",
+        "sys_err_logg",
+        "lim_logg",
+        
+        "feh",
+        "e_feh",
+        "e_pos_feh",
+        "e_neg_feh",
+        "nn_nodes_feh",
+        "nn_spectra_feh",
+        "enn_feh",
+        "nne_feh",
+        "sys_err_feh",
+        
+        "xi",
+        "e_xi",
+        "e_pos_xi",
+        "e_neg_xi",
+        "nn_nodes_xi",
+        "nn_spectra_xi",
+        "enn_xi",
+        "nne_xi",
+        
+        "mh",
+        "e_mh",
+        "e_pos_mh",
+        "e_neg_mh",
+        "nn_nodes_mh",
+        "nn_spectra_mh",
+        "enn_mh",
+        "nne_mh",
+
+        "alpha_fe",
+        "e_alpha_fe",
+        "e_pos_alpha_fe",
+        "e_neg_alpha_fe",
+        "nn_nodes_alpha_fe",
[…]

### 2016-10-11 sandbox_plot.py

@@ -3,6 +3,10 @@
 from code.model import ensemble, plot
 
 
+
+raise a
+
+
 for wg in (11, ):
 
     for parameter in ("teff", "logg", "feh"):

### 2016-10-11 sandbox_plot_wg_performance.py

@@ -1,0 +1,99 @@
+
+import yaml
+from glob import glob
+
+from code import (GESDatabase, plot, summary)
+from astropy.table import Table
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+# Clean up bits and pieces...
+
+
+savefig_kwds = dict(dpi=300, bbox_inches="tight")
+
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+
+isochrones = glob("isochrones/*.dat")
+
+debug = True
+
+for wg in (11, ):
+
+
+    # Plot clusters.
+
+    # Plot against clusters.
+    cluster_velocities = Table.read("fits-templates/oc_gc_radial_vel.dat", format="ascii")
+
+    for isochrone in isochrones:
+        cluster = isochrone.split("/")[-1].split("_")[0]
+        if cluster == "gamma2-Vel":
+            cluster = "gamma2_Vel"
+
+        match = cluster_velocities["id"] == cluster
+        if not any(match):
+            vel_range = None
+
+        else:
+            vrad = cluster_velocities["rv"][match]
+            e_vrad = cluster_velocities["erv"][match]
+            vel_range = (vrad - 2*e_vrad, vrad + 2*e_vrad)
+            vel_range = (vel_range[0][0], vel_range[1][0])
+
+        try:
+
+            fig = plot.cluster(database, cluster, wg,
+                isochrone_filename=isochrone, vel_range=vel_range)
+
+        except:
+            if debug: raise
+            logger.exception(
+                "Could not create cluster {} figure for {}:".format(cluster, wg))
+
+        else:
+            if fig is not None:
+                basename = "figures/wg{wg}/wg{wg}-cluster-{cluster}".format(
+                    wg=wg, cluster=cluster)
+
+                fig.savefig("{}.pdf".format(basename), **savefig_kwds)
+                fig.savefig("{}.png".format(basename), **savefig_kwds)
+
+
+
+        try:
+            fig = plot.cluster(database, cluster, wg,
+                isochrone_filename=isochrone, vel_range=vel_range,
+                limit_to_isochrone_range=True)
+
[…]

### 2016-10-11 scripts/homogenise_fast.py

@@ -12,7 +12,7 @@ from collections import OrderedDict
 
 
 from code import GESDatabase
-from code.model.ensemble import EnsembleModel
+from code.model.ensemble import EnsembleModel, MedianModel
 
 # Initialize logging.
 logger = logging.getLogger("ges")
@@ -42,6 +42,13 @@ sample_kwds = dict(chains=4, iter=10000, thin=10)
 
 finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
 benchmarks = benchmarks[finite]
+
+model = MedianModel(database, 11, "xi")
+model.homogenise_all_stars(update_database=True, default_sigma=0.5)
+
+model = MedianModel(database, 11, "alpha_fe")
+model.homogenise_all_stars(update_database=True, default_sigma=0.10)
+
 
 models = {}
 for wg in wgs:

### 2016-10-11 scripts/ship_wg11.py

@@ -1,0 +1,32 @@
+
+"""
+Ship a WG11 recommended SP product.
+"""
+
+import yaml
+import logging
+
+from code import GESDatabase, ship
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+
+# Produce a per CNAME file.
+ship.wg_recommended_sp_template(database,
+    "fits-templates/recommended-templates/GES_iDR5_WG11_RecommendedTemplate_16072016.fits",
+    "outputs/GES_iDR5_WG11_Recommended.fits",
+    11, overwrite=True)
+
+
+# Produce a PER-SETUP file even though they will be duplicates.
+ship.wg_recommended_sp_template(database,
+    "fits-templates/recommended-templates/GES_iDR5_WG11_RecommendedTemplate_16072016_PERSETUP.fits",
+    "outputs/GES_iDR5_WG11_Recommended_PERSETUP.fits",
+    11, overwrite=True)

### 2016-10-12 code/model/ensemble.py
Switch to polynomial model for systematic uncertainties, not exponential

@@ -406,7 +406,7 @@ class BaseEnsembleModel(object):
         return None
 
 
-    def _load_model(self, recompile, overwrite, path=None):
+    def _load_model(self, recompile=False, overwrite=False, path=None, **kwargs):
         """
         Load the model.
 
@@ -421,6 +421,9 @@ class BaseEnsembleModel(object):
             `self._MODEL_PATH`
         """
 
+        if getattr(self, "_model", None) is not None:
+            return self._model
+
         # Is the model already compiled?
         path = path or self._MODEL_PATH
         compiled_path = "{}.compiled".format(path)
@@ -431,10 +434,9 @@ class BaseEnsembleModel(object):
                 model = pickle.load(fp)
 
             # Check that the model code is the same as what we expected.
-            with open(path, "r") as fp:
-                model_code = fp.read()
-
-            if model_code != model.model_code:
+            assert self._model_code is not None
+            
+            if self._model_code != model.model_code:
                 logger.warn("Pre-compiled model differs to the code in {}; "\
                     "re-compiling".format(path))
                 recompile = True
@@ -446,15 +448,16 @@ class BaseEnsembleModel(object):
                 break
 
         else:
-            logger.info("Compiling model from {}".format(path))
+            logger.info("Compiling model")
 
-            model = stan.StanModel(file=path)
+            model = stan.StanModel(model_code=self._model_code)
 
             # Save the compiled model.
             if not os.path.exists(compiled_path) or overwrite:
                 with open(compiled_path, "wb") as fp:
                     pickle.dump(model, fp, -1)
 
+        self._model = model
         return model
 
 
@@ -513,6 +516,8 @@ class BaseEnsembleModel(object):
             Overwrite the compiled model path if it already exists.
         """
 
+        self._load_model(recompile=recompile, overwrite=overwrite, **kwargs)
+
         kwds = self._validate_stan_inputs(data=data, **kwargs)
         return self._model.optimizing(**kwds)
 
@@ -546,6 +551,8 @@ class BaseEnsembleModel(object):
         :param overwrite: [optional]
             Overwrite the compiled model path if it already exists.
         """
+
+        self._load_model(recompile=recompile, overwrite=overwrite, **kwargs)
 
         kwds = self._validate_stan_inputs(
             data=data, chains=chains, iter=iter, warmup=warmup, **kwargs)

### 2016-10-12 scripts/homogenise_fast.py

@@ -43,12 +43,13 @@ sample_kwds = dict(chains=4, iter=10000, thin=10)
 finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
 benchmarks = benchmarks[finite]
 
+"""
 model = MedianModel(database, 11, "xi")
 model.homogenise_all_stars(update_database=True, default_sigma=0.5)
 
 model = MedianModel(database, 11, "alpha_fe")
 model.homogenise_all_stars(update_database=True, default_sigma=0.10)
-
+"""
 
 models = {}
 for wg in wgs:
@@ -71,15 +72,31 @@ for wg in wgs:
                     data["lower_bound"], data["upper_bound"], size=data["TM"]),
                 "alpha_sq": np.mean([data["lower_alpha_sq"], data["upper_alpha_sq"]]) * np.ones(data["N"]),
                 "vs_c": scale**2 * np.ones(data["N"]),
-                "vs_a": 1e-2 + np.zeros((data["N"], data["S"])).T,
-                "vs_b": 1e-2 + np.ones((data["N"], data["S"])).T,
+                #"vs_a": 1e-2 + np.zeros((data["N"], data["S"])).T,
+                #"vs_b": 1e-2 + np.ones((data["N"], data["S"])).T,
+                "vs_theta": 1e-2 + np.zeros((9, data["N"])),
                 "L_corr": np.eye(data["N"])
             }
+
+            init.update({"vs_tb{}".format(i): 1 for i in range(1, 9)})
+            init.update({"vs_lb{}".format(i): 1 for i in range(1, 9)})
+            init.update({"vs_fb{}".format(i): 1 for i in range(1, 9)})
+
+            init.update({"vs_ta{}".format(i): 2 for i in range(1, 9)})
+            init.update({"vs_la{}".format(i): 2 for i in range(1, 9)})
+            init.update({"vs_fa{}".format(i): 2 for i in range(1, 9)})
+            
+            init["vs_tc7"] = 1 * np.ones(data["N"])
+            init["vs_tc8"] = 1 * np.ones(data["N"])
+            init["vs_tc9"] = 1 * np.ones(data["N"])
+
 
             print("Number of model parameters: {}".format(
                 sum([np.array(v).size for v in init.values()])))
 
             op_params = model.optimize(data, init=init, iter=100000)
+
+            raise a
 
             fit = model.sample(data, init=op_params, **sample_kwds)
 

### 2016-10-12 code/model/ensemble.py
add framework for match by cname

@@ -913,3 +913,218 @@ class EnsembleModel(BaseEnsembleModel):
         result = (data_dict, metadata)
         self._data, self._metadata = result
         return result
+
+
+
+class CNAMEEnsembleModel(EnsembleModel):
+
+    _MODEL_PATH = os.path.join(
+        os.path.dirname(os.path.realpath(__file__)),
+        "ensemble-model.stan")
+
+    def _prepare_data(self, parameter=None, default_sigma_calibrator=1e3,
+        minimum_node_estimates=1, sql_constraint=None):
+        """
+        Prepare the data for the model so that it can be supplied to Stan.
+
+        :param parameter: [optional]
+            The name of the model parameter (e.g., teff) that will be used in
+            this single parameter ensemble model. If `None` provided, then this
+            defaults to the model parameter provided when the EnsembleModel was
+            initiated.
+
+        :param minimum_node_estimates: [optional]
+            The minimum number of node measurements for a single visit of a 
+            calibrator spectrum. If this is set to a negative value, then only
+            calibrator results will be used where *all* nodes have provided a
+            measurement for that spectrum.
+
+        :param sql_constraint: [optional]
+            Specify an optional SQL constraint to include when retrieving the
+            node results.
+        """
+
+        parameter = str(parameter or self._parameter).lower()
+        valid_parameters = ["teff", "logg", "feh"]
+        if parameter not in valid_parameters:
+            raise AreYouSureYouKnowWhatYoureDoing
+
+        # Get the data from the database for this WG.
+        calibrator_cnames = self._calibrators["CNAME"]
+
+        data = self._database.retrieve_table(
+            """ WITH    n AS (
+                            SELECT id FROM nodes WHERE wg = {wg}), 
+                SELECT DISTINCT ON (r.filename, r.node_id) 
+                    s.cname, s.ges_type, s.ges_fld,
+                    r.filename, r.node_id, r.snr,
+                    r.{parameter}, r.e_{parameter}
+                FROM    n, results as r 
+                WHERE   TRIM(r.cname) in ({calibrator_cnames})
+                  AND   r.node_id = n.id 
+                  AND   r.passed_quality_control = true {sql_constraint}
+                """.format(
+                    wg=self._wg, parameter=parameter,
+                    sql_constraint=""   if sql_constraint is None \
[…]

### 2016-10-13 scripts/homogenise_all_wgs.py
things

@@ -12,7 +12,7 @@ from collections import OrderedDict
 
 
 from code import GESDatabase
-from code.model.ensemble import  SingleParameterEnsembleModel
+from code.model.ensemble import  SingleParameterEnsembleModel, EnsembleModelWithSysVarianceModel
 
 # Initialize logging.
 logger = logging.getLogger("ges")
@@ -40,7 +40,8 @@ parameter_scales = OrderedDict([
 
 sample_kwds = dict(chains=4, iter=2000)
 
-benchmarks = benchmarks[(benchmarks["FEH"] > -2) * (benchmarks["TEFF"] > 4000)]
+finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
+benchmarks = benchmarks[finite]
 
 models = {}
 for wg in wgs:
@@ -53,39 +54,39 @@ for wg in wgs:
             model = SingleParameterEnsembleModel.read(model_path, database)
 
         else:
-            model = SingleParameterEnsembleModel(database, wg, parameter, benchmarks)
+            model = EnsembleModelWithSysVarianceModel(database, wg, parameter, benchmarks)
             data, metadata = model._prepare_data(default_sigma_calibrator=scale)
 
             init = {
+                # -1 offset to account for Stan's 1-indexing.
                 "truths": data["mu_calibrator"],
-                "var_sys_estimator": (scale/5.)**2 * np.ones(data["N_estimators"]),
+                #"var_sys_estimator": (scale/5.)**2 * np.ones(data["N_estimators"]),
                 "alpha": np.mean([data["lower_alpha"], data["upper_alpha"]]) \
                     * np.ones(data["N_estimators"]),
                 "rho_estimators": np.zeros(metadata["N_pairwise_estimators"]),
-                "c0_estimators": np.zeros(data["N_estimators"])
+                "c0_estimators": np.zeros(data["N_estimators"]),
+
             }
 
+            init["vs_log_c"] = np.log(np.ones(data["N_estimators"]) * scale)
+            init["vs_a"] = np.ones(data["N_estimators"])
+            init["vs_b"] = 2 * np.ones(data["N_estimators"])
+
+            raise a
             op_params = model.optimize(data, init=init, iter=100000)
 
+            raise a
             fit = model.sample(data, init=op_params, **sample_kwds)
 
             model.write(model_path, overwrite=True)
 
+        # Keep the model.
+        models[wg][parameter] = model
 
[…]

### 2016-10-13 scripts/homogenise_fast.py

@@ -38,7 +38,7 @@ parameter_scales = OrderedDict([
     ("feh", 0.25)
 ])
 
-sample_kwds = dict(chains=4, iter=10000, thin=10)
+sample_kwds = dict(chains=2, iter=2000)
 
 finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
 benchmarks = benchmarks[finite]

### 2016-10-14 code/model/ensemble.py
Update ensemble model to homogenise using the poly Stan model

@@ -122,7 +122,7 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
         ["feh", (-3, 0.5)],
     ])
     xs = np.clip(
-        [(np.nanmedian(estimates[p]) - l)/(u - l) for p, (l, u) in bounds.items()],
+        [1.0 - (np.nanmedian(estimates[p]) - l)/(u - l) for p, (l, u) in bounds.items()],
         0, 1)
 
     for ii, i in enumerate(indices):
@@ -149,9 +149,21 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
 
             spectrum_snr = np.clip(estimates["snr"][s:e], 1, 500)
             
-            var_node_sys[j] = samples["vs_c"][i, j] * np.exp(np.sum([
-                samples["vs_a"][i, l, k] * pow(1 - xs[l], samples["vs_b"][i, l, k]) \
-                    for l in range(len(xs))]))
+            
+            #var_node_sys[j] = samples["vs_c"][i, j] * np.exp(np.sum([
+            #    samples["vs_a"][i, l, k] * pow(1 - xs[l], samples["vs_b"][i, l, k]) \
+            #        for l in range(len(xs))]))
+            var_node_sys[j] = samples["vs_c"][i, k] * (4.0 
+                + samples["vs_ta{}".format(k + 1)][i] * xs[0]**2
+                + samples["vs_la{}".format(k + 1)][i] * xs[1]**2
+                + samples["vs_fa{}".format(k + 1)][i] * xs[2]**2
+                + samples["vs_tb{}".format(k + 1)][i] * xs[0]
+                + samples["vs_lb{}".format(k + 1)][i] * xs[1]
+                + samples["vs_fb{}".format(k + 1)][i] * xs[2]
+                + samples["vs_tc7"][i, k] * xs[0] * xs[1]
+                + samples["vs_tc8"][i, k] * xs[0] * xs[2]
+                + samples["vs_tc9"][i, k] * xs[1] * xs[2]
+            )
 
 
             diag_variance = (samples["alpha_sq"][i, k]/spectrum_snr) \
@@ -228,30 +240,30 @@ def _homogenise_survey_measurements(database, wg, parameter, cname, N=100,
 
         record = database.retrieve(
             """ SELECT id
-                  FROM wg_recommended_results
+                  FROM wg_recommended_results_poly_sys
                  WHERE wg = %s
                    AND cname = %s
             """, (wg, cname, ))
 
         if record:
[…]

### 2016-10-14 code/model/plot.py

@@ -310,7 +310,7 @@ def node_uncertainty_with_snr(model, quartiles=[16, 50, 84], show_cr_bound=True,
 
     ax.set_ylim(ylims)
     
-    legend_kwds = dict(loc="upper center", ncol=2, frameon=False)
+    legend_kwds = dict(fontsize=10, loc="upper center", ncol=2, frameon=False)
     legend_kwds.update(kwargs.get("legend_kwds", {}))
     plt.legend(**legend_kwds)
     

### 2016-10-14 code/plot/benchmarks.py

@@ -47,9 +47,11 @@ def node_benchmark_performance(database, wg, node_name, sort_by="TEFF",
     benchmarks = benchmarks[ok]
 
 
-    fig, axes = plt.subplots(3, figsize=(16.5, 7.5))
     parameters = ("teff", "logg", "mh")
     fits_parameters = ("TEFF", "LOGG", "FEH")
+    
+    fig, axes = plt.subplots(3, figsize=(16.5, 7.5))
+    
     ylabels = {
         "teff": r"$\Delta{}T_{\rm eff}$ $({\rm K})$",
         "logg": r"$\Delta\log{g}$",
@@ -205,7 +207,8 @@ def wg_benchmark_performance(database, wg, truths, show_recommended=False,
     ylims = ylims or {}
 
     parameters = kwargs.get("parameters", ("TEFF", "LOGG", "FEH"))
-    fig, axes = plt.subplots(len(parameters), figsize=(16.5, 7.5))
+    fig, axes = plt.subplots(
+        len(parameters), figsize=kwargs.get("figsize", (12, 2.5 * len(parameters))))
     
     default_ylabels = {
         "TEFF": r"$\Delta{}T_{\rm eff}$ $({\rm K})$",
@@ -234,7 +237,9 @@ def wg_benchmark_performance(database, wg, truths, show_recommended=False,
             kwds = dict(
                 parameter=parameter, wg=wg, ges_fld=benchmark["GES_FLD"].strip(),
                 node_sql_constraint_str=" AND {}".format(node_sql_constraint) \
-                    if node_sql_constraint is not None else "")
+                    if node_sql_constraint is not None else "",
+                recommended_table=kwargs.get(
+                    "recommended_table", "wg_recommended_results"))
 
             node_estimates = database.retrieve_table(
                 """ SELECT DISTINCT ON (results.id)
@@ -263,7 +268,7 @@ def wg_benchmark_performance(database, wg, truths, show_recommended=False,
                 wg_recommended = database.retrieve_table(
                     """ SELECT  {parameter}, e_{parameter}, 
                                 e_pos_{parameter}, e_neg_{parameter}
-                          FROM  wg_recommended_results as wgr, spectra
+                          FROM  {recommended_table} as wgr, spectra
                          WHERE  wgr.wg = {wg}
                            AND  wgr.cname = spectra.cname
                            AND  TRIM(spectra.ges_fld) = '{ges_fld}';
[…]

### 2016-10-14 sandbox_plot.py
Sandbox updates

@@ -4,15 +4,23 @@ from code.model import ensemble, plot
 
 
 
-raise a
-
-
 for wg in (11, ):
 
-    for parameter in ("teff", "logg", "feh"):
+    for parameter in ("logg", ):# ("teff", "logg", "feh"):
 
         model = ensemble.EnsembleModel.read(
-            "homogenisation-wg11-{}.model".format(parameter), None)
+            "good-exponential-models-master/homogenisation-wg11-{}.model".format(parameter), None)
+
+        # Plot the random uncertainty as a function of SNR
+        fig = plot.node_uncertainty_with_snr(model)
+        
+        raise a
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-random-{param}.pdf"\
+            .format(wg=wg, param=parameter))
+        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-random-{param}.png"\
+            .format(wg=wg, param=parameter))
+
+
 
         # Plot the distribution of biases for each node
         fig = plot.biases(model)
@@ -22,12 +30,7 @@ for wg in (11, ):
             wg=wg, param=parameter))
         
 
-        # Plot the random uncertainty as a function of SNR
-        fig = plot.node_uncertainty_with_snr(model)
-        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-random-{param}.pdf"\
-            .format(wg=wg, param=parameter))
-        fig.savefig("figures/wg{wg}/wg{wg}-node-uncertainty-random-{param}.png"\
-            .format(wg=wg, param=parameter))
+
 
         # Plot the relative systematic uncertainty as a function of parameters
         fig = plot.node_relative_systematic_uncertainty(model)

### 2016-10-14 sandbox_plot_wg_performance.py

@@ -25,6 +25,22 @@ debug = True
 
 for wg in (11, ):
 
+    raise a
+    
+    # Plot benchmarks first.
+    fig = plot.wg_benchmark_performance(database, wg, benchmarks, 
+        show_recommended=True, ylims=dict(TEFF=1000, LOGG=1, FEH=1))
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.pdf".format(wg=wg), **savefig_kwds)
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.png".format(wg=wg), **savefig_kwds)
+
+
+    fig = plot.wg_benchmark_performance(
+        database, wg, benchmarks, show_recommended=True)
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks.pdf".format(wg=wg), **savefig_kwds)
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks.png".format(wg=wg), **savefig_kwds)
+
+    raise a
+
 
     # Plot clusters.
 
@@ -85,15 +101,3 @@ for wg in (11, ):
                 fig.savefig("{}.png".format(basename), **savefig_kwds)
 
     raise a
-
-    # Plot benchmarks first.
-    fig = plot.wg_benchmark_performance(database, wg, benchmarks, 
-        show_recommended=True, ylims=dict(TEFF=1000, LOGG=1, FEH=1))
-    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.pdf".format(wg=wg), **savefig_kwds)
-    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.png".format(wg=wg), **savefig_kwds)
-
-
-    fig = plot.wg_benchmark_performance(
-        database, wg, benchmarks, show_recommended=True)
-    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks.pdf".format(wg=wg), **savefig_kwds)
-    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks.png".format(wg=wg), **savefig_kwds)

### 2016-10-14 scripts/homogenise_fast.py

@@ -57,8 +57,12 @@ for wg in wgs:
     for parameter, scale in parameter_scales.items():
 
         model_path = model_paths.format(wg=wg, parameter=parameter)
+        model_path = "homogenisation-wg{wg}-{parameter}-poly-sys.model".format(
+            wg=wg, parameter=parameter)
+
         if os.path.exists(model_path): 
             model = EnsembleModel.read(model_path, database)
+            continue
 
         else:
             model = EnsembleModel(database, wg, parameter, benchmarks)
@@ -91,20 +95,18 @@ for wg in wgs:
             init["vs_tc9"] = 1 * np.ones(data["N"])
 
 
-            print("Number of model parameters: {}".format(
+            print("Number of model parameters for {}: {}".format(parameter,
                 sum([np.array(v).size for v in init.values()])))
 
             op_params = model.optimize(data, init=init, iter=100000)
-
-            raise a
 
             fit = model.sample(data, init=op_params, **sample_kwds)
 
             model.write(model_path, 
                 overwrite=True, __ignore_model_pars=("Sigma", "full_rank_estimates"))
 
-
-        model.homogenise_all_stars(update_database=True)
+        #raise a
+        #model.homogenise_all_stars(update_database=True)
 
 
 # TODO:

### 2016-10-14 article/ms.tex
Add some paragraphs about technical flags

@@
 
+\subsection{Technical flags}
+\label{sec:technical-flags}
+
+In the fifth \gaiaeso\ data release we required all analysis nodes to either
+supply results for a spectrum, or to provide a technical flag (column \texttt{TECH})
+explaining no results were reported. We list all relevant technical flags and their
+interpretation in Appendix \ref{app:flags}. There is a large variation in specificity 
+between flags. For example, some flags indicate that an analysis pipeline did not 
+converge (for whatever reason), whereas some flags indicate a result is uncertain 
+due to a data reduction issue producing a `picket-fence'-like pattern in the 
+spectrum. The former is provided automatically and may reflect uncertainty 
+\emph{only} in the results from the node who reported the flag. However, the latter 
+example was presumably flagged because a human looked at the data, and this flag
+should raise uncertainty in \emph{all} results using the same spectrum.  Similar 
+examples can be drawn for flags describing issues intrinsic to the star (e.g., high
+rotational velocity), and not just a single spectrum.  For these reasons, there are 
+situations where technical flags ought to be propagated to other results derived from 
+the same spectrum, or other results reported for the same star.
+
+We investigated usage patterns between nodes to evaluate whether any flag propagation
+was warranted. A heatmap of common flag usage for WG11 nodes is shown in Figure
+\ref{fig:wg11-flag-heatmap}.
+% TODO: Include heat maps of other WGs?
+If all nodes reported the same flags under common conditions, then the node-to-node 
+segments in Figure \ref{fig:wg11-flag-heatmap} would show 1-to-1 correlations. This is 
+not the case; we find the flag usage to be mostly uncorrelated between different nodes. 
+When one node reports a \emph{specific} flag indicating an issue that is intrinsic to 
+the spectrum or star, it is highly unlikely that \emph{any} other node has reported the 
+same problem.\footnote{In some sense, this is a consequence of having `many eyes on the 
+data'.} The most significant correlations are seen in the usage of non-descript flags,
+where nodes will report that the derived stellar parameters are outside of the range 
+where they consider their results to be `physically realistic' (e.g., outside of a grid
+or the effective temperature $\teff$ is too high or low to be reliable).
+
+Based on our examination of technical flag usage between nodes, we assigned every node 
+result with a boolean flag indicating whether the supplied node results ($\teff$, $\logg$,
+$\feh$) should be used in the homogenisation process.\footnote{This flag is only present
+in an internal PostgreSQL database, which also includes the propagated flag explaining
+why a record should not be used in the homogenisation process, and which record the flag
+originated from.}  We did not use any results that were marked with any of the technical
+flags listed in Table \ref{tab:wg11-node-specific-flags-failing-qc}.  We further discarded 
+results flagged as having $v\sin{i} > 20$~km~s$^{-1}$ (flags 11020 and 11050) unless the 
+reporting node was OACT, as our examination (over multiple data releases) revealed that 
+the OACT node can properly account for fast rotating stars, whereas some nodes may not 
+even detect the presence of significant rotation.
+
+We discarded results from IACAIP that were flagged to be an incomplete spectrum or 
+missing wavelengths (flag 10105), as IACAIP seemingly used this flag extensively to 
+indicate \emph{any} problem with their own analysis.  For all other nodes that report
+flag 10105, we propagated this flag to all results derived from the same spectrum,
+and discarded those node estimates.  However, if \emph{any} node reported one of the
+data reduction issues in Table \ref{tab:wg11-spectrum-specific-flags-failing-qc}
+(e.g., saturated or broken spectrum, poor sky subtraction) then we propagated this 
+flag to other results derived from the same spectrum, and discarded those results.
+For stars with multiple observations, we were also able to identify situations where 
+all nodes reported significantly different stellar parameters, all in the same 
+systematic direction (e.g., $\teff$ values reported by all nodes were $\sim$300~K for 
+one spectrum). In all cases, these systematic differences arose from archival spectra. 
+A visual inspection of these spectra revealed substantial data reduction issues, and 
+therefore we discarded all results derived from these problematic spectra.  Finally, 
+we discarded \emph{all} node results for a star (matched by \texttt{CNAME}) if any of 
+the spectra were flagged -- by any node -- as being a suspected multiple stellar system 
+(10320, 13027, or 20020). The total fraction of WG11 records that were discarded due to
+flags, including propagated flags, is 23.7\% (11,553 of 48,720), however only 580 unique 
+stars analysed by WG11 had all results discarded due to flag usage (of 4,941; 11.7\%).
+
+%FIGURE: wg11-flag-heatmap: Show 2D matrix heatmap of flag usage by WG11 nodes
+
+%TABLE IN APPENDIX \label{app:flags}: <no-name>: List of all relevant flags and their meaning.
+
+%TABLE IN APPENDIX \label{app:flags}: wg11-node-specific-flags-failing-qc: List of node-specific flags that caused us to discard results.
+Note in the caption the conditions for OACT & vsini, as well as IACAIP with missing wavelengths.
+
+%TABLE IN APPEDIX \label{app:flags}: wg11-spectrum-specific-flags-failing-qc: List of spectrum-specific flags that caused us to discard results.
+Note in the caption that we did something unusual for IACAIP.
+
 % Stellar parameter homogenisation
@@
 \label{sec:stellar-parameter-homogenisation}
-
-Flag propagation.
 
@@
 This inference problem is numerically unstable, as there are many model parameters
-which are used toi
-
- construct a covariance matrix that is sampled
-
-In practice
+AND TODO
 we include the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $\rho$

### 2016-10-14 article/ms.tex
foo
stuff

@@
 
-\begin{itemize}
+\begin{enumerate}
     \item   \emph{The uncertainties reported by each node are incorrect.}
@@
 
-            \noindent{}where $\epsilon$ represents the noise in the estimate.
+            \noindent{}where $\epsilon$ represents the noise in the estimate. As per
+            assumption (1), we assert that the distribution of $\epsilon$ is unknown
+            for each node.
 
     \item   \emph{The unbiased stellar parameters from any two nodes are correlated.}
-            After accounting for individual node biases, we assume that the 
-            stellar parameters reported by any two nodes will be correlated
-            to some degree. The level of correlation between two nodes is unknown.
+            After accounting for individual node biases, we assume that the stellar 
+            parameters reported by any two nodes will be correlated to some degree. 
+            The level of correlation between two nodes is unknown \emph{a priori}.
             This assumption arises from commonalities that led to the estimates from
             each node. Specifically: all nodes are instructed to use a common list 
-            of line transitions, the same MARCS model photospheres, some nodes employ
-            similar methods (e.g., spectral synthesis), and all nodes derive their 
-            estimates from the same data (in some instances, even the same 
-            continuum-normalized spectra are used).
+            of line transitions, the same MARCS model photospheres. Moreover, some 
+            nodes employ similar methods (e.g., spectral synthesis), and importantly
+            \emph{all} nodes derive their estimates from the same data (in some 
+            instances, even the same continuum-normalized spectra are used).
 
@@
 
-    \item   \emph{There are gaps in the data.} 
+    \item   \emph{There are missing data.} 
             No spectrum is guaranteed to have stellar parameters reported by all
@@
             space explored. If stellar parameters are not reported, then the reason 
-            must be specified through a \texttt{TECH} flag (see Section \ref{sec:flags}
-            on flag usage).
+            must be specified with a technical flag (\texttt{TECH}; see Section 
+            \ref{sec:technical-flags}).
 
@@
             decreasing S/N ratio.}
+            Specifically we assume that the random uncertainty $\sigma_{rand}$ will
+            increase as,
+
+            \begin{eqnarray}
+                \sigma_{rand,node} = \frac{\alpha_{node}}{\sqrt{S/N}}
+            \end{eqnarray}
+
+            \noindent{}where $S/N$ is the signal-to-noise ratio, and $\alpha$ is
+            unknown for each node.
 
@@
 
-\end{itemize}
+\end{enumerate}
 

### 2016-11-29 article/ms.tex
Add words about flag propagation

--- 2016-10-11 article/ms.tex
@@
 % Stellar parameter homogenisation
+
+\subsection{Flag propagation}
+\label{sec:flag-propagation}
+
+In earlier data releases the analysis nodes were \emph{encouraged} to submit flags that
+describe technicalities that may have affected their analysis, or peculiar issues
+that were identified in a star or spectrum.  These flags proved invaluable in enabling 
+homogenisation leads to identify scenarios where particular pipelines perform poorly. 
+For example, OACT (WG11) were able to identify and account for high rotation, whereas 
+ULB (WG11) would not identify fast rotators, and ULB (WG11) would report significantly
+noisier stellar parameters for fast rotators.
+
+From DR5 onwards, these examples led to the decision to \emph{require} analysis nodes 
+to submit stellar parameters ($\teff$, $\logg$, [Fe/H], and $\xi$ where appropriate),
+for every spectrum, or supply a technical flag explaining why no stellar parameters
+could be derived (preferably supply both when appropriate). The full list of flags used
+in DR5 is listed in Appendix \ref{appendix:flags}.  In Figures \ref{fig:flag-propagation-wg10}
+and \ref{fig:flag-propagation-wg11} we show heatmaps of flag usage between different 
+analysis nodes in WG10 and WG11, respectively.  If all nodes reported the same flags then
+a one-to-one density mapping would be visible.  Note that here we are only showing instances
+where multiple flags have been reported for a single spectrum: for the sake of clarity we
+do not show situations where only one flag is reported by a single node.  Figures 
+\ref{fig:flag-propagation-wg10} and \ref{fig:flag-propagation-wg11} demonstrate that when one analysis node reports a flag, it
+is highly unlikely that the same issue has been reported by another node. The most common
+situation is that one node will report a descriptive flag (e.g., \texttt{10106} 
+to indicate a broken spectrum containing a picket-fence or Heaviside pattern), and other
+nodes will report a non-specific flag (e.g., \texttt{10302}: code convergence issue).
+
+We constructed a sequence of rules to propagate detailed flag information to other results.
+We categorised these rules to propagate to results that were derived from either the same 
+spectrum (e.g., \texttt{10106} broken spectrum), or the same star (e.g., suspected binary 
+star system).  These propagation rules are listed in Tables \ref{tab:flag-propagation-spectrum}
+and \ref{tab:flag-propagation-cname}. Any results with propagated technical flags were 
+marked as failing internally quality control standards, and were not used in the homogenisation
+process.  Results with any of the flags listed in Table \ref{tab:node-specific-flags} were
+were also excluded from homogenisation, however those flags were considered `node-specific'
+in that they do not necessarily require propagation to other results derived from the same
+spectrum or star.
+
+We also excluded all cluster records (\texttt{GES\_TYPE} of 'XX-XX-XX' or `XX-XX-XX') 
+reported by OACT (WG11).  Although OACT performed excellently in the benchmark and blind tests
+in WG11, we identified convergence issues in cluster field, which consequently altered the
+metallicity scale of globular clusters.
+
+% Any other exclusions? WG10 IAC results at edges?
+
+The total number of records (set of $\teff$, $\logg$, [Fe/H]) that were marked as failing
+internal quality controls due to reported or propagated flags were XXX for WG10 and XXX for
+WG11.  This represents a small fraction of the total number of records submitted in each
+working group (XXX\% for WG10 and XXX\% for WG11).
+The number of stars (unique \texttt{CNAME}s) where all results were excluded due to reported or propagated flags was XXX for WG10 and XXX for WG11.
+These cases were principally due to data reduction issues (e.g., flags
+\texttt{10100-10150}), and these examples were supplied to the data reduction group to
+examine before the sixth data release.
+
 \subsection{Stellar parameter homogenisation}
@@
 
-Flag propagation.
-
-\noindent{}We make the following assumptions when constructing a model for homogenisation:
+\noindent{}We make the following assumptions in our homogenisation model:
 
@@
 is the number of correlation coefficients between all nodes.\footnote{
-This inference problem is numerically unstable, as there are many model parameters
-which are used toi
-
- construct a covariance matrix that is sampled
-
-In practice
-we include the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $\rho$
-as model parameters instead of directly modeling the $\rho$ terms.  The correlation
-matrix can be reconstructed by $\rho = (IL)\cdot(IL)^T$ where $I$ is the $N \times N$
-identity matrix. This parameterisation helps ensure that the resulting covariance
-matrix $\mathbf{\Sigma}$ is positive semi-definite, and can therefore be used for
-sampling.}
+This inference problem is numerically unstable because a \emph{positive semi-definite}
+covariance matrix must be constructed from the model parameters in every MCMC draw, 
+and there is no joint prior available to ensure that the positive semi-definite 
+condition is met.  Although there are parameterisations that will help enforce 
+this condition \citep{Pinheiro:1996}, in practice we found that including 
+the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $K$ as model
+parameters --- instead of directly modelling the set of node correlation 
+coefficients $\{\rho\}$ --- was sufficient to ensure positive-semidefinite 
+covariance matrices and produce sensible solutions.  The correlation matrix can 
+then be reconstructed by $K = (IL)\cdot(IL)^T$ where $I$ is the $N \times N$ identity
+matrix.  This representation implies a uniform prior on all correlation coefficients
+$p\left(\rho\right) = \mathcal{U}\left(-1, +1\right)$.}
 
@@
 
+\begin{thebibliography}{}
+\bibitem[Pinheiro \& Bates(1996)]{Pinheiro:1996} Pinheiro, J.~C., \& Bates, D.~M.\ 1996, Statistics and Computing, 6, 3
+
+\end{thebibliography}
+
 \end{document}

### 2017-02-06 article/ms.tex
yolo

@@
 \newcommand{\acronym}[1]{{\small{#1}}}
+\newcommand{\project}[1]{\textsl{#1}}
+\newcommand{\article}{\textit{Article}}
 
 \newcommand{\ges}{\acronym{GES}}
-\newcommand{\project}[1]{\textsl{#1}}
-
 \newcommand{\gaiaeso}{\project{Gaia-ESO}}
@@
 \begin{document}
-\title{The Gaia-ESO Survey: Combined estimates from multiple stellar analysis pipelines}
+\title{The \gaiaeso\ Survey: Combined estimates from multiple stellar analysis pipelines}
 
@@
 \begin{abstract}
-  Some stuff
+	% The GES scientific goals
+	% GES has a unique analysis strategy.
+	% Allows XYZ benefits.
+	% Here we describe the process for homogenisation of stellar parameters for FGK-type
+	% stars analysed with both UVES and GIRAFFE data, in order to produce recommended results.
+	% We construct a noise model for each node, and infer error behaviour for each node as a
+	% function of S/N and stellar parameters.
+	% We combine these to produce results.
+	% For the first time, we describe blind tests conducted in GES to examine subjectivity, etc.
+	% The typical reported uncertainties in stellar parameters are XYZ
+	% We outline a list of recommended best practices and lessons learned for stellar parameter determination
+	% We provide a common, homogeneous metallicity scale for GCs and OCs, and demonstrate that GES results can be used to infer diffusion/settling in clusters??
+	% Other potential science highlights:
+	% --> Something with velocity/metallicity in the field? two-point correlation function.
+	% --> High-/low-alpha sequence with GIRAFFE stuff.
+
 \end{abstract}
@@
 
-% Multiple analysis strategy: why
+The unique parallel analysis strategy adopted by the \ges\ provides a number of
+benefits over other spectroscopic surveys.  We can identify the strengths and
+weaknesses of state-of-the-art analysis methods, quantify the systematic 
+differences that arise from \emph{defensible analysis decisions}, and produce an 
+unbiased estimator of stellar parameters with representative uncertainties that account
+for both random and systematic contributions.  Although this procedure requires an
+enormous amount of collaboration and coordination, it is necessary to provide
+a thorough evaluation of systematic uncertainties present between analysis 
+pipelines that are routinely used in the literature.
 
-% primary advantage and disadvantage to multiple analysis strategy
+We perform the \ges\ spectroscopic analysis for each data release in two 
+consecutive rounds.  In the first round, the stellar parameters are reported by
+each analysis group.  The homogenisation of stellar parameters is performed by the
+working group leads (WG10, WG11, WG12, WG13), and the recommended results from each
+working group are submitted to the top-level homogenisation group, WG15. WG15 makes
+checks to ensure the results from different working groups are on the same scale, 
+and combines the results from multiple working groups to produce a single set of 
+\emph{Survey}-level recommended stellar parameters for each star \citep{Hourihane:2017}.
+These recommended results are used in the second analysis round, where individual 
+nodes report detailed chemical abundances given the recommended stellar parameters.
+In this \article\ we describe only the first round of analysis; the homogenisation 
+of detailed chemical abundances for FGK-type stars will be described in a companion 
+contribution (Casey et al., 2017).
 
-% Description of two parameter rounds: stellar parameters, abundances
+\subsection{Analysis methods}
+\label{sec:analysis-nodes}
+% How many nodes contributed to DR5 in WG11/WG10, and how many results did they provide per setup? (what fraction?)
 
-% What's reported by each node? Flags? Consistency of flags?
-
-% Description of pipelines in appendix
-
-% Commonalities between nodes: model atmospheres, line list, normalized spectra, initial params, spectrum library, xi calibration if necessary.
+% Summary description of nodes
+% What do the nodes provide? Most parameters, flags, etc.
+% Detailed description of pipelines in appendix
 
@@
 
-% What do the nodes provide? Most parameters, flags, etc.
+\subsubsection{Summary of (dis-)similarities in analysis methods}
+\label{sec:analysis-node-similarities}
 
-% CONTINUE from here:
-% Stellar parameter determination
+Despite the multiple analysis strategies adopted in \ges, there are a number of
+commonalities between the nodes. Specifically, all FGK-analysis nodes use the same:
+\begin{enumerate}
+  \item Updated MARCS model photospheres \citep{BG}.
+  \item Atomic and molecular line lists, updated with recently measured oscillator strengths \citep{Heiter:2016,someone}.
+  \item Rest-frame, pseudo-continuum-normalised spectra are provided to all nodes by the data reduction group.
+Individual echelle orders are also provided.
+Inverse variance arrays are available for all flux arrays.
+  \item Initial stellar parameters are provided for all stars observed with GIRAFFE.
+  \item Infrared photometry is available for all targets.
+  \item For methods that perform template-fitting, all nodes are provided with a grid of high-resolution continuum-normalised spectra synthesised using (1) and (2).
+The synthetic grid covers the entire wavelength region used for \ges.
+  \item Where relevant, nodes are provided with empirical microturbulence calibrations for main-sequence, sub-giant, and giant stars. These relations are given in Appendix \ref{app:xi}.
+\end{enumerate}
 
-% Stellar parameter homogenisation
+There are three caveats to the listed items above.  Firstly, while nodes are encouraged
+to use the same empirically-scaled interpolator for photospheric models \citep{Masseron:2006},
+this is not required.  Secondly, the nodes are not required to use the 
+pseudo-continuum-normalised spectra provided to them; each node can chose to 
+adopt their own continuum normalisation procedure.  Lastly, although all nodes use the 
+same atomic and molecular data, the nodes are free to chose \emph{which} lines (or 
+spectral regions) to use when fitting their models to the data.
+
+In summary, the analysis nodes generally differ only in \emph{defensible analysis decisions}:
+there is no well-founded \emph{a priori} reason that would explain why one method should be
+significantly better or worse across the space of stellar parameters.  For these reasons,
+the Gaia-ESO Survey is well-placed to critically examine what analysis decisions will
+objectively result in more accurate or precise results.
 
@@
             This assumption arises from commonalities that led to the estimates from
-            each node. Specifically: all nodes are instructed to use a common list 
-            of line transitions, the same MARCS model photospheres, some nodes employ
-            similar methods (e.g., spectral synthesis), and all nodes derive their 
-            estimates from the same data (in some instances, even the same 
-            continuum-normalized spectra are used).
+            each node (Section \ref{sec:analysis-node-similarities}).
 
-            We note that even two nodes with identical methods are not guaranteed
+            We reiterate that even two nodes with identical methods are not guaranteed
             to be perfectly correlated, because the \emph{choice} of which transitions
@@
             \gaiaeso: no node or method is expert across the entire range of parameter
-            space explored. If stellar parameters are not reported, then the reason 
-            must be specified through a \texttt{TECH} flag (see Section \ref{sec:flags}
-            on flag usage).
+            space explored.
 
@@
     \item   \emph{All `well-studied' stars have noisy measurement, and their values
-            are not known with infinite precision.} But we assume they are unbiased!
+            are not known with infinite precision.} That is to say, we assume that there
+            are some well-studied stars with unbiased measurements, but those
+            measurements are noisy. For this reason, we must include the stellar
+            parameters of each well-studied star as a model parameter, and use 
+            non-spectroscopic data to place a strong prior on that stellar parameter.
 
@@
 
+\newpage
+\appendix
+\section{Microturbulence calibrations} \label{app:xi}
+
+% Version 2.0 taken from http://great.ast.cam.ac.uk/GESwiki/GesWg/GesWg11/Microturbulence
+
+The following microturbulence calibrations were recommended for nodes to use where appropriate. For main-sequence or sub-giant stars with $\teff >= 5000$~K and $\logg >= 3.5$,
+
+\begin{equation}
+\xi = 1.05 + 2.51\times10^{-4}(\teff T_0) + 1.5\times10^{-7}(\teff - T_0)^2 - 0.14(\logg - g_0) - 0.005(\logg - g_0)^2 + 0.05\feh + 0.01\feh^2 \quad ,
+\end{equation}
+
+\noindent{}and for main-sequence or sub-giant stars with $\teff < 5000$~K,
+
+\begin{equation}
+\xi = 1.05 + 2.51\times10^{-4}(5000 - T_0) + 1.5\times10^{-7}(5000 - T_0)^2 - 0.14(\logg - g_0) - 0.005(\logg - g_0)^2 + 0.05\feh + 0.01\feh^2 \quad ,
+\end{equation}
+
+\noindent{}and for giant stars:
+
+\begin{equation}
+\xi = 1.25 + 4.01\times10^{-4}(\teff - T_0) + 3.1\times10^{-7}(\teff - T_0)^2 - 0.14(\logg - g_0) - 0.05(\logg - g_0)^2 + 0.05\feh + 0.01\feh^2 \quad .
+\end{equation}
+
+\noindent{}In all three cases above: $T_0 = 5500$~K and $g_0 = 4.0$.
+
+\section{Flags} \label{app:flags}
+
+\section{\texttt{Stan} code for homogenisation noise model} \label{app:stan-code}
+
 \end{document}

### 2017-02-06 code/model/combined.py

@@ -141,11 +141,24 @@ class BaseCombinedModel(object):
         if not kwds.pop("validate", True):
             return kwds
 
-        # Check chains and init values.
-        if "init" in kwds.keys() and isinstance(kwds["init"], dict) \
-        and kwds.get("chains", 1) > 1:
+        init = kwds.pop("init", None)
+        
+        if isinstance(init, dict):
+            for key in init.keys():
+                try:
+                    # Check for zero length array.
+                    s = init[key].size
+                
+                except:
+                    continue
 
-            init, chains = (kwds["init"], kwds.get("chains", 1))
+                else:
+                    if s == 1:
+                        init[key] = np.atleast_1d(init[key])
+
+        # Check chains
+        chains = kwds.get("chains", 1)
+        if chains > 1:
             logger.info(
                 "Re-specifying initial values to be list of dictionaries, "\
                 "allowing one dictionary per chain ({}). "\
@@ -153,6 +166,10 @@ class BaseCombinedModel(object):
                 .format(chains))
             
             kwds["init"] = [init] * chains
+        
+        else:
+            kwds["init"] = init
+
 
         if kwargs.get("data", None) is None:
             try:
@@ -231,6 +248,13 @@ class BaseCombinedModel(object):
         ignore_model_pars = kwargs.get("__ignore_model_pars", ("Sigma", ))
         model_pars = set(self._fit.model_pars).difference(ignore_model_pars)
         self._chains = self._fit.extract(pars=model_pars)
+
+        # Check that the chains are the right shape, etc.
+        if len(self._chains["biases"].shape) == 1:
+
+            # Single node only. Ensure that the posteriors are the right shape.
+            for key in ("systematic_variance", "alpha_sq", "biases", "alpha"):
+                self._chains[key] = np.atleast_2d(self._chains[key]).T
 
         return None
 
@@ -320,7 +344,7 @@ class CombinedModel(BaseCombinedModel):
 
     
     def _get_mapping_coefficients_from_calibrators(self, vector_terms, 
-        sql_constraint=None):
+        sql_constraint=None, **kwargs):
         """
         Map individual node results to the calibrators.
 
@@ -380,7 +404,7 @@ class CombinedModel(BaseCombinedModel):
 
         # Get the data in a nice format and match to the benchmark value.
         calibrators = self._calibrators.copy()
-        calibrator_ges_flds = np.array(map(str.strip, calibrators["GES_FLD"]))
[…]

### 2017-02-06 code/model/ensemble.py

@@ -418,8 +418,10 @@ class BaseEnsembleModel(object):
 
         model_code = kwargs.get("model_code", None)
         if model_code is None:
-            with open(self._MODEL_PATH, "r") as fp:
+            model_path = kwargs.get("model_path", self._MODEL_PATH)
+            with open(model_path, "r") as fp:
                 model_code = fp.read()
+            self._MODEL_PATH = model_path
 
         self._model_code = model_code
         

### 2017-02-06 code/plot/__init__.py

@@ -4,3 +4,4 @@ from clusters import *
 from nodes import *
 from benchmarks import *
 import flags
+import blind

### 2017-02-06 code/plot/benchmarks.py

@@ -99,8 +99,7 @@ def node_benchmark_performance(database, wg, node_name, sort_by="TEFF",
         N += np.hstack(diff).size
         bp = ax.boxplot(diff, widths=width, patch_artist=True)
         ax.set_xlim(-0.5, len(benchmarks) + 0.5)
-        raise CHECKTHIS
-
+        
         ax.set_ylabel(ylabels.get(parameter))
         ylim = ylims.get(parameter, None)
         if ylim is not None:
@@ -152,6 +151,7 @@ def node_benchmark_performance(database, wg, node_name, sort_by="TEFF",
 
 def wg_benchmark_performance(database, wg, truths, show_recommended=False,
     sort_by=None, ylims=None, node_sql_constraint=None, skip_missing=True,
+    recommended_sql_constraint=None,
     show_num_estimates=None, xlabels=None, ylabels=None, **kwargs):
     """
     Show a box-and-whisker plot for the benchmark parameters reported by a given
@@ -202,6 +202,7 @@ def wg_benchmark_performance(database, wg, truths, show_recommended=False,
     width = kwargs.get("width", 0.45)
     colors = kwargs.get("colors", ("#000000", "#4daf4a", "#e41a1c"))
 
+    
     show_num_estimates = True if ylims is None or show_num_estimates else False
     xlabels = xlabels or {}
     ylims = ylims or {}
@@ -238,6 +239,8 @@ def wg_benchmark_performance(database, wg, truths, show_recommended=False,
                 parameter=parameter, wg=wg, ges_fld=benchmark["GES_FLD"].strip(),
                 node_sql_constraint_str=" AND {}".format(node_sql_constraint) \
                     if node_sql_constraint is not None else "",
+                recommended_sql_constraint_str = "" if recommended_sql_constraint is None \
+                                    else " AND {} ".format(recommended_sql_constraint),
                 recommended_table=kwargs.get(
                     "recommended_table", "wg_recommended_results"))
 
@@ -271,7 +274,8 @@ def wg_benchmark_performance(database, wg, truths, show_recommended=False,
                           FROM  {recommended_table} as wgr, spectra
                          WHERE  wgr.wg = {wg}
                            AND  wgr.cname = spectra.cname
-                           AND  TRIM(spectra.ges_fld) = '{ges_fld}';
+                           AND  TRIM(spectra.ges_fld) = '{ges_fld}'
+                           {recommended_sql_constraint_str};
                     """.format(**kwds))
 
                 if wg_recommended is None:

### 2017-02-06 code/plot/cluster.py

@@ -105,7 +105,7 @@ def param_vs_param(database, wg, node_name, ges_fld, reference_parameter,
 
 def cluster(database, ges_fld, wg, node_name=None, vel_range=None,
     isochrone_filename=None, limit_to_isochrone_range=False, ax=None,
-    no_tech_flags=False, show_legend=True, **kwargs):
+    no_tech_flags=False, show_legend=True, sql_constraint=None, **kwargs):
     """
     Show a Hertzsprung-Russell diagram for cluster stars, with isochrones
     optionally shown.
@@ -151,11 +151,11 @@ def cluster(database, ges_fld, wg, node_name=None, vel_range=None,
         # Get the data.
         table = "results"
         node_id = database.retrieve_node_id(wg, node_name)
-        sql_constraint = "AND r.node_id = '{}'".format(node_id)
+        table_constraint = "AND r.node_id = '{}'".format(node_id)
 
     else:
         table = "wg_recommended_results"
-        sql_constraint = "AND r.wg = '{}'".format(wg)
+        table_constraint = "AND r.wg = '{}'".format(wg)
 
     
     if no_tech_flags:
@@ -174,9 +174,12 @@ def cluster(database, ges_fld, wg, node_name=None, vel_range=None,
                 AND TRIM(s.ges_fld) = '{ges_fld}'
                 AND s.vel > '{lower_vel}'
                 AND s.vel < '{upper_vel}'
-                {sql_constraint} {tech_flag_constraint}""".format(
+                {sql_constraint}
+                {table_constraint} {tech_flag_constraint}""".format(
                     table=table, ges_fld=ges_fld, 
-                    sql_constraint=sql_constraint,
+                    sql_constraint="" if sql_constraint is None \
+                                      else " AND {} ".format(sql_constraint),
+                    table_constraint=table_constraint,
                     tech_flag_constraint=tech_flag_constraint,
                     lower_vel=min(vel_range), upper_vel=max(vel_range)))
 

### 2017-02-06 code/plot/clusters.py

@@ -75,7 +75,7 @@ def hertzsprung_russell_diagrams(database, cluster_names=None,
         all WGs will be shown.
     """
 
-
+    isochrone_filenames = isochrone_filenames or {}
     velocity_constraints = velocity_constraints or {}
     
     if cluster_names is None:
@@ -85,12 +85,13 @@ def hertzsprung_russell_diagrams(database, cluster_names=None,
         cluster_names = sorted(
             cluster_names, key=lambda k: literature.get(k, -np.inf))
 
-    sql_constraint = "" if sql_constraint is None else " AND {}".format(sql_constraint)
+    sql_constraint = "" if sql_constraint is None else " AND ({})".format(sql_constraint)
 
     #"#e74c3c"
 
     default_styles = {
         10: dict(facecolor="#e67e22"), #1abc9c"),
+        110: dict(facecolor="#e67e22"), #1abc9c"),
         11: dict(facecolor="#2ecc71",),
         12: dict(facecolor="#3498db",),
         13: dict(facecolor="#9b59b6",),
@@ -112,15 +113,20 @@ def hertzsprung_russell_diagrams(database, cluster_names=None,
     for i, (ax, cluster_name) in enumerate(zip(axes, cluster_names)):
 
         # Get the data for this cluster.
-        candidates = database.retrieve_table(
-            """ SELECT  s.vel, r.wg, 
-                        r.teff, r.logg, r.feh, 
-                        r.e_teff, r.e_logg, r.e_feh
-                  FROM  wg_recommended_results AS r, spectra AS s
-                 WHERE  s.cname = r.cname
-                   AND  r.teff <> 'NaN' AND r.logg <> 'NaN' AND r.feh <> 'NaN'
-                   AND  s.ges_fld = '{}' {}""".format(cluster_name, sql_constraint))
-
+        candidates = database.retrieve_table("""
+            WITH s  AS (
+                SELECT cname, vel FROM spectra WHERE ges_fld = '{ges_fld}')
+            SELECT DISTINCT ON (r.id)
+                    r.id, r.wg, r.cname, r.setup, r.filename, s.vel,
+                    r.teff, r.logg, r.feh,
+                    r.e_teff, r.e_logg, r.e_feh,
+                    r.nn_nodes_teff, r.nn_nodes_logg, r.nn_nodes_feh,
+                    r.nn_spectra_teff, r.nn_spectra_logg, r.nn_spectra_feh
+            FROM    wg_recommended_results AS r, s
[…]

### 2017-02-06 code/plot/utils.py

@@ -10,11 +10,18 @@ def parse_isochrone(filename):
         The filename of the isochrone.
     """
 
+    is_new_parsec = "parsec2.9" in filename.lower()
+
     is_parsec = "parsec" in filename.lower()
     kwds = {
         "format": "ascii"
     }
-    if is_parsec:
+    if is_new_parsec:
+        kwds.update({
+            "data_start": 0,
+            "header_start": 5
+        })
+    elif is_parsec:
         kwds.update({
             "data_start": 0,
             "header_start": 13
@@ -23,7 +30,11 @@ def parse_isochrone(filename):
     isochrone = Table.read(filename, **kwds)
 
     # Make columns common.
-    if is_parsec:
+    if is_new_parsec:
+        # Fuck you girardi
+        isochrone["teff"] = 10**isochrone["logTe"]
+
+    elif is_parsec:
         isochrone["logg"] = isochrone["logG"]
         isochrone["teff"] = 10**isochrone["logTe"]
 

### 2017-02-06 code/ship.py

@@ -14,7 +14,7 @@ logger = logging.getLogger("ges")
 
 
 def wg_recommended_sp_template(database, input_path, output_path, wg,
-    ext=-1, overwrite=False, **kwargs):
+    ext=-1, overwrite=False, match_by_setup=False, **kwargs):
     """
     Produce a WG-recommended file of stellar parameters from the template 
     provided (on a per CNAME) basis.
@@ -128,11 +128,14 @@ def wg_recommended_sp_template(database, input_path, output_path, wg,
         logger.info("At row {}/{}: {}".format(i + 1, N, cname))
 
         record = database.retrieve_table(
-            """ SELECT {columns}
+            """ SELECT setup, {columns}
                   FROM wg_recommended_results
                  WHERE wg = '{wg}'
                    AND cname = '{cname}'
-            """.format(wg=wg, cname=cname, columns=", ".join(columns)))
+                   {setup_constraint}
+            """.format(wg=wg, cname=cname, columns=", ".join(columns),
+                setup_constraint="" if not match_by_setup \
+                                    else "AND TRIM(setup) = '{}'".format(image[ext].data["SETUP"][i])))
 
         if record is None:
             # Keep whatever is currently there in the template.

### 2017-02-06 sandbox_plot_wg_clusters.py

@@ -41,7 +41,7 @@ velocity_constraints = {
 
 metallicity_constraints = {
     "M15": (-5, -0.50),
-    "NGC4372": (-3, -1),
+    "NGC4372": (-3, -2.0),
     #"NGC4833": (-2.50, -1.75),
     "M2": (-5, -1.30), #--> check
     #-->"NGC1904": (-1.70, -1.00),
@@ -67,8 +67,30 @@ fig = plot.wg_metallicity_overview(database, x_axis="logg",
     ptp_ylim=None, sql_constraint="((s.wg = 10 and r.nn_nodes_teff > 1 and r.snr > 10 and r.teff > 4000 and r.teff < 6500) or (s.wg != 10))")
 """
 
+
+isochrone_filenames = {
+    "M15":     "isochrones/M15_Parsec_12Gyr_Z0.0001.dat",
+    "NGC4372": "isochrones/NGC4372_Parsec2.9_10Gyr_Z0.0001.dat",
+    "M2": "isochrones/M2_Parsec2.9_12Gyr_Z0.00034.dat",
+    "NGC1904": "isochrones/NGC1904_Parsec2.9_12Gyr_Z0.00038.dat",
+    "NGC6752": "isochrones/NGC6752_Parsec2.9_12Gyr_Z0.000438.dat",
+    "M12": "isochrones/M12_Parsec2.9_12Gyr_Z0.000648.dat",
+    "NGC1261": "isochrones/NGC1261_Parsec2.9_12Gyr_Z0.000816.dat",
+    "NGC362": "isochrones/NGC362_Parsec2.9_12Gyr_Z0.000816.dat",
+    "NGC1851": "isochrones/NGC1851_Parsec2.9_12Gyr_Z0.001.dat",
+    "NGC2808": "isochrones/NGC2808_Parsec2.9_12Gyr_Z0.0011.dat",
+    "NGC104": "isochrones/NGC104_Parsec2.9_12Gyr_Z0.002896.dat",
+    "NGC5927": "isochrones/NGC5927_Parsec2.9_12Gyr_Z0.00491.dat",
+    "NGC6553": "isochrones/NGC6553_Parsec2.9_12Gyr_Z0.01.dat",
+    "NGC4833": "isochrones/NGC4833_Parsec_12Gyr_Z0.0002.dat",
+    "NGC5927": "isochrones/NGC5927_Parsec_11Gyr_Z0.004.dat",
[…]

### 2017-02-06 sandbox_plot_wg_performance.py

@@ -26,7 +26,11 @@ debug = True
 
 cluster_velocities = Table.read("fits-templates/oc_gc_radial_vel.dat", format="ascii")
 
-for wg in (10, 11, 20, ):
+
+for wg in (10, ):
+
+    sql_constraint = "TRIM(r.SETUP) = 'HR10|HR21'"
+
 
     for isochrone in isochrones:
 
@@ -47,56 +51,62 @@ for wg in (10, 11, 20, ):
         try:
 
             fig = plot.cluster(database, cluster, wg,
-                isochrone_filename=isochrone, vel_range=vel_range)
+                isochrone_filename=isochrone, vel_range=vel_range,
+                sql_constraint=sql_constraint)
 
         except:
             if debug: raise
-            logger.exception(
+            print(
                 "Could not create cluster {} figure for {}:".format(cluster, wg))
 
         else:
             if fig is not None:
-                basename = "figures/wg{wg}/wg{wg}-cluster-{cluster}-poly".format(
+                basename = "figures/wg{wg}/wg{wg}-cluster-{cluster}".format(
                     wg=wg, cluster=cluster)
 
                 fig.savefig("{}.pdf".format(basename), **savefig_kwds)
                 fig.savefig("{}.png".format(basename), **savefig_kwds)
-
+                print("Created figure {}.pdf".format(basename))
+                
 
 
         try:
             fig = plot.cluster(database, cluster, wg,
                 isochrone_filename=isochrone, vel_range=vel_range,
-                limit_to_isochrone_range=True)
+                limit_to_isochrone_range=True,
+                sql_constraint=sql_constraint)
 
         except:
             if debug: raise
-            logger.exception(
+            print(
                 "Could not create cluster {} figure for {}:".format(cluster, wg))
 
         else:
             if fig is not None:
-                basename = "figures/wg{wg}/wg{wg}-cluster-{cluster}-limited-poly"\
+                basename = "figures/wg{wg}/wg{wg}-cluster-{cluster}-limited"\
                             .format(wg=wg, cluster=cluster)
 
                 fig.savefig("{}.pdf".format(basename), **savefig_kwds)
[…]

### 2017-02-06 sandbox_plotting.py

@@ -29,7 +29,7 @@ database = GESDatabase(**credentials)
 
 
 debug = False
-wgs = (10, 11, 12, 13)
+wgs = (10, )#11, 12, 13)
 parameters = ("teff", "logg", "mh", "xi")
 isochrones = glob("isochrones/*.dat")
 
@@ -38,7 +38,7 @@ isochrones = glob("isochrones/*.dat")
 
 
 # Create node-level folders.
-nodes = database.retrieve_table("SELECT id, wg, TRIM(name) as name FROM nodes")
+nodes = database.retrieve_table("SELECT id, wg, TRIM(name) as name FROM nodes WHERE wg in %s", (wgs, ))
 for node in nodes:
     folder = "figures/qc/wg{}/{}".format(node["wg"], node["name"])
     if not os.path.exists(folder):

### 2017-02-06 scripts/ges_dr5_wg10_homogenise_recio-blanco.py

@@ -58,6 +58,15 @@ node_submissions = \
 # Create a table that we will use to put in the homogenised values.
 homogenised_table = first_submission.copy()
 
+# Specify the parameters to homogenise.
+parameters = ("TEFF", "LOGG", "FEH")
+
+# Put all the PARAMETER (and E_PARAMETER) columns as NaNs
+for parameter in parameters:
+    homogenised_table[parameter] = np.nan
+    homogenised_table["E_{}".format(parameter)] = np.nan
+
+
 # Select a high-quality sub-sample of common stars between all nodes where the
 # SNR > 15, and within reasonable ranges.
 
@@ -83,15 +92,13 @@ all_transformation_subset_requirements = {
     ]
 }
 
-# Specify the parameters to homogenise.
-parameters = ("TEFF", "LOGG", "FEH")
 
 # We will reference the group indices from the first node submission.
 group_indices = node_submissions[0].groups.indices
 for index in range(group_indices.size - 1):
     gi, gj = group_indices[index:index + 2]
 
-    setup = node_submissions[0]["SETUP"][gi]
+    setup = node_submissions[0]["SETUP"][gi].strip()
 
     # Only consider the results from this setup.
     only_consider = np.zeros(len(first_submission), dtype=bool)
@@ -101,11 +108,6 @@ for index in range(group_indices.size - 1):
 
     if setup not in all_transformation_subset_requirements:
         print("Skipping stars with SETUP = {0}".format(setup))
-
-        # Put all the PARAMETER (and E_PARAMETER) columns as NaNs
-        for parameter in parameters:
-            homogenised_table[parameter][only_consider] = np.nan
-            homogenised_table["E_{}".format(parameter)][only_consider] = np.nan
 
         # Continue to the next setup.
         continue
@@ -281,6 +283,11 @@ for index in range(group_indices.size - 1):
     fig.tight_layout()
     fig.savefig(
         "ges-dr5-wg10-{0}-recio-blanco-calibration-comparison.pdf".format(setup))
+    fig.savefig(
+        "ges-dr5-wg10-{0}-recio-blanco-calibration-comparison.png".format(setup),
+        dpi=100)
+
+
 
     # Produce a homogenised set of values using the pre-calculated weights.
     for parameter, w in weights.items():
@@ -288,7 +295,12 @@ for index in range(group_indices.size - 1):
             node_submission["CALIBRATED_{}".format(parameter)][only_consider] \
             for node_submission in node_submissions])
 
+
[…]

### 2017-02-06 scripts/ingest_wg10_temp.py

@@ -27,7 +27,7 @@ with open(db_filename, "r") as fp:
 database = GESDatabase(**credentials)
 
 # Ingest shitty WG10 results
-data = Table.read("recommended-results/GES_iDR5_WG10_Recommended_PERSETUP.fits")
+data = Table.read("recommended-results/GES_iDR5_WG10_RecommendedTemplate_14072016_PERSETUP.fits")
 
 
 
@@ -192,6 +192,8 @@ N = len(data.groups)
 for i, group in enumerate(data.groups):
 
     row = group[0]
+    if row["SETUP"] != "HR10|HR21": continue
+    
     """
     hr1021 = np.where(group["SETUP"] == "HR10|HR21")[0]
     if not hr1021:

### 2017-02-06 scripts/propagate_flags.py

@@ -1,8 +1,6 @@
 #!/usr/bin/python
 
-"""
-Propagate relevant flag information from one node to others.
-"""
+""" Mark results as poor quality based on submitted flag information. """
 
 import logging
 import yaml
@@ -23,8 +21,6 @@ logger = logging.getLogger("ges")
 with open("flags.yaml", "r") as fp:
     qc_flags = yaml.load(fp)
 
-raise a
-
 
 # Clear any previous propagations before starting.
 logger.info("Clearing previous propagations and setting all to have passed_quality_control = True")
@@ -37,52 +33,8 @@ database.update(
                 propagated_peculi = '',
                 propagated_remark = '',
                 passed_quality_control = true
-         WHERE  passed_quality_control = false;""")
-
-
-
-
-database.connection.commit()
-
-# Identify spurious spectra and mark them as such.
-N_peculiar_spectra = {}
-peculiar_spectra_kwds = dict(
-    and_or="and", sigma_discrepant=3, teff_discrepant=250, logg_discrepant=0.25)
-
-for wg in (10, 11, 12, 13):
-
-    logger.info("Querying for peculiar spectra in WG{}".format(wg))
-
-    kwds = dict(wg=wg)
-    kwds.update(peculiar_spectra_kwds)
-
-    peculiar_spectrum_query = """
-        with t4 as (
[…]

### 2017-02-06 scripts/setup_db.py

@@ -59,10 +59,11 @@ for wg, node_names in all_nodes.items():
 N_ingested = database.ingest_spectra_masterlist(masterlist_filename)
 
 # Ingest results from the nodes.
-for filename in glob("node-results/stellar-parameters/WG??/GES_iDR5_WG??_*.fits"):
+for filename in glob("node-results/stellar-parameters/WG10/GES_iDR5_WG??_*.fits"):
     N = database.ingest_node_results(filename, extension=1)
     logger.info("Ingested {} results from {}".format(N, filename))
 
+raise a
 
 # Ingest additional photometric temperatures from Laura Magrini.
 #for filename in glob("fits-templates/additional-tphots-magrini/*.fits"):

### 2017-02-06 code/plot/blind.py
yolo2

@@ -1,0 +1,653 @@
+
+"""
+Produce figures related to the blind tests.
+"""
+
+import logging
+import numpy as np
+import os
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import yaml
+from matplotlib.ticker import MaxNLocator
+from matplotlib import gridspec
+from astropy.table import Table
+from collections import Counter, OrderedDict
+
+import utils
+
+__all__ = []
+
+logger = logging.getLogger("ges.idr5")
+
+def _retrieve_blind_test_result(database, original_filename, blind_filename,
+    additional_columns=None, sql_constraint=None):
+    """
+    Retrieve a blind test result.
+
+    :param original_filename:
+        The original filename.
+
+    :param blind_filename:
+        The blind filename that was used in the test.
+
+    :param sql_constraint: [optional]
+        Any additional SQL constraint to place on the query.
+
+    :returns:
+        A two-length tuple containing a table of results based on the original
+        filename, and a table of results based on the blind filename. If no
+        results were available for either query, then `None` will be returned
+        instead of a table.
+    """
+
+    sql_constraint \
+        = "" if sql_constraint is None else "AND {}".format(sql_constraint)
+
+    # Get the original and blind CNAMEs first.
+    #original_cname, blind_cname = [database.retrieve(
+    #    """ SELECT cname
+    #        FROM spectra 
+    #        WHERE filename LIKE '%{}%';""".format(os.path.basename(path)))[0][0] \
+    #    for path in (original_filename, blind_filename)]
+
+    # Get results for each.
+    # Add columns that we need for reasons.
+    columns = [
+        "node_id", "nodes.name", "nodes.wg", 
+        "teff", "e_teff", "logg", "e_logg", "feh", "e_feh",
+        "trim(results.tech) as tech"]
+    if additional_columns is not None:
+        columns = list(set(columns + list(additional_columns)))
+
+    original_results = database.retrieve_table(
+        """ SELECT DISTINCT ON (results.id) {columns}
+            FROM results, nodes, spectra
+            WHERE results.cname = spectra.cname
+              AND results.filename LIKE '%{basename}%'
+              AND results.node_id = nodes.id
+            {sql_constraint};""".format(
+                basename=os.path.basename(original_filename),
+                columns=", ".join(columns),
+                sql_constraint=sql_constraint))
+
+    blind_results = database.retrieve_table(
+        """ SELECT DISTINCT ON (results.id) {columns}
[…]

### 2017-02-06 scripts/homogenise_combined.py

@@ -1,0 +1,101 @@
+
+"""
+A script to homogenise Gaia-ESO Survey data using a combined model,
+one that maps node results onto a common scale before inferring their
+relative contributions and correlations using a noise model.
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase
+from code.model.combined import CombinedModel
+
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+# Enable autocommit mode so that we can do homogenisation in parallel
+database.connection.autocommit = True
+
+# Load the "benchmarks"
+# Only use "benchmarks" with TEFF < 8000 K
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+benchmarks["E_FEH"] = 0.10
+
+model_paths = "homogenisation-wg{wg}-{parameter}-{setup}-combined.model"
+
+wgs = (10, )
+parameter_scales = OrderedDict([
+    ("teff", 250),
+    ("logg", 0.25),
+    ("feh", 0.25)
+])
+
+
+sample_kwds = dict(chains=2, iter=4000)
+
+finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
+benchmarks = benchmarks[finite]
+
+for wg in wgs:
+    for setup in ("HR10", "HR21", "HR10|HR21"):
+
+        for parameter, default_sigma_calibrator in parameter_scales.items():
+
+            model_path = model_paths.format(
+                wg=wg, parameter=parameter, setup=setup.replace("|", "_"))
+            
+            if os.path.exists(model_path): 
+                model = CombinedModel.read(model_path, database)
+                
+            else:
+                model = CombinedModel(database, wg, parameter, benchmarks)
+
+                data, metadata = model._prepare_data(
+                    default_sigma_calibrator=default_sigma_calibrator, 
+                    minimum_node_estimates=1,
+                    sql_constraint="TRIM(name) LIKE '%-{}'".format(setup))
+
+
+                init = {
+                    "truths": data["mu_calibrator"],
+                    "biases": np.zeros(data["N"]),
[…]

### 2017-02-06 scripts/homogenise_combined_wg11.py

@@ -1,0 +1,101 @@
+
+"""
+A script to homogenise Gaia-ESO Survey WG11 data using a combined model,
+one that maps node results onto a common scale before inferring their
+relative contributions and correlations using a noise model.
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase
+from code.model.combined import CombinedModel
+
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+# Enable autocommit mode so that we can do homogenisation in parallel
+database.connection.autocommit = True
+
+# Load the "benchmarks"
+# Only use "benchmarks" with TEFF < 8000 K
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+benchmarks["E_FEH"] = 0.10
+
+model_paths = "homogenisation-wg{wg}-{parameter}-combined-wrt-bm.model"
+
+wg = 11
+parameter_scales = OrderedDict([
+    ("teff", 250),
+    #("logg", 0.25),
+    #("feh", 0.25)
+])
+
+vector_terms = [
+    (("teff", ), 1),
+    (("logg", ), 1),
+    (("feh", ), 1),
+]
+
+sample_kwds = dict(chains=2, iter=4000)
+
+finite = np.isfinite(benchmarks["TEFF"] * benchmarks["LOGG"] * benchmarks["FEH"])
+benchmarks = benchmarks[finite]
+
+
+for parameter, default_sigma_calibrator in parameter_scales.items():
+
+    model_path = model_paths.format(wg=wg, parameter=parameter)
+
+    if os.path.exists(model_path): 
+        model = CombinedModel.read(model_path, database)
+        
+    else:
+        model = CombinedModel(database, wg, parameter, benchmarks)
+
+        data, metadata = model._prepare_mapped_data(
+            vector_terms, 
+            reference_node_id=None,
+            default_sigma_calibrator=default_sigma_calibrator, 
+            minimum_node_estimates=5,
+            sql_constraint=None)
+
+        init = {
+            "truths": data["mu_calibrator"],
[…]

### 2017-02-06 scripts/homogenise_wg20.py

@@ -1,0 +1,161 @@
+
+"""
+Homogenise the results from "WG20" (WG10 HR15N)
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase
+from code.model.ensemble import EnsembleModel, MedianModel
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+CHECK_FOR_NODE_SETUPS = False
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+# Give new node names to all WG10 nodes on a per-setup basis?
+if CHECK_FOR_NODE_SETUPS:
+
+    distinct_nodes = database.retrieve_table(
+        """select distinct on (name, node_id, setup) name, node_id, setup from results, nodes where results.node_id = nodes.id and nodes.wg = 20 and results.teff <> 'NaN'""")
+
+    if not np.all(["-" in name for name in distinct_nodes["name"]]):
+        logger.info("Creating new nodes!")
+
+        for distinct_node in distinct_nodes:
+            new_node_name = "{}-{}".format(distinct_node["name"].strip(), distinct_node["setup"].strip())
+            new_node_id = database.create_or_retrieve_node_id(10, new_node_name)
+
+            # Update all the results.
+            logger.info("Updating to {}/{}".format(new_node_id, new_node_name))
+            N = database.update(
+                "UPDATE results SET node_id = '{}' WHERE node_id = '{}';".format(
+                    new_node_id, distinct_node["node_id"]))
+            
+            print(N)
+
+        database.connection.commit()
+
+# Load the "benchmarks"
+# Only use "benchmarks" with TEFF < 8000 K
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+benchmarks["E_FEH"] = 0.10
+
+model_paths = "homogenisation-wg{wg}-{parameter}.model"
+
+
+wgs = (20, )
+
+parameter_scales = OrderedDict([
+    ("teff", 250),
+    ("logg", 0.25),
+    ("feh", 0.25),
+
+])
+
+sample_kwds = dict(chains=4, iter=5000)
+
[…]

### 2017-02-06 scripts/map_wg10_nodes.py

@@ -1,0 +1,185 @@
+
+"""
+Test different mappings between WG10 nodes.
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase
+from code.model.combined import CombinedModel
+
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+
+# Assign the nodes new names first.
+old_nodes = database.retrieve_table("""
+    SELECT DISTINCT ON (nodes.name, setup) nodes.id, nodes.name, setup
+    FROM results, nodes
+    WHERE results.node_id = nodes.id
+      AND nodes.wg = 10
+      AND results.teff <> 'NaN'""")
+
+for old_node in old_nodes:
+
+    if "-" in old_node["name"]:
+        print("Skipping {}".format(old_node["name"]))
+        continue
+
+    new_node_name = "{name}-{setup}".format(
+        name=old_node["name"], setup=old_node["setup"].strip())
+
+    new_node_id = database.create_or_retrieve_node_id(10, new_node_name)
+
+    N = database.update("""
+        UPDATE results 
+        SET node_id = %s
+        WHERE node_id = %s
+          AND TRIM(setup) = %s;
+        """, (new_node_id, old_node["id"], old_node["setup"].strip()))
+
+    print(old_node["id"], old_node["name"], old_node["setup"].strip(), N)
+
+
+# Only use "benchmarks" with TEFF < 8000 K
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+benchmarks["E_FEH"] = 0.10
+
+# Do everything except Nice first.
+vector_terms = {
+    "teff":[
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+    ],
+    "logg": [
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+    ],
+    "feh": [
+        (("feh", ), 1),
+    ]
+
+}
+
+reference_nodes = {
[…]

### 2017-02-06 scripts/plot_blind_test.py

@@ -1,0 +1,90 @@
+
+"""
+Make plots from the blind test.
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase, plot
+
+logger = logging.getLogger("ges")
+
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+# Load benchmark truths
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+
+# Load giraffe blind spectra.
+blind_giraffe = Table.read("fits-templates/blind-test/blind-test-giraffe.txt",
+    format="ascii", names=("original", "blind"))
+blind_giraffe = [(original, blind) for original, blind in \
+    zip(blind_giraffe["original"], blind_giraffe["blind"])]
+
+
+blind_uves = Table.read("fits-templates/blind-test/blind-test-uves.txt",
+    format="ascii", names=("original", "blind"))
+blind_uves = [(original, blind) for original, blind in \
+    zip(blind_uves["original"], blind_uves["blind"])]
+
+
+fig_uves = plot.blind.explain_differences(database, blind_uves,
+    __comparison_filename="ges-dr5-uves-blind-test-comparison.fits",
+    group_by=("wg", "name"))
+fig_uves.savefig("figures/blind-test/ges-dr5-uves-blind-test-explaination.pdf", dpi=150)
+fig_uves.savefig("figures/blind-test/ges-dr5-uves-blind-test-explaination.png", dpi=150)
+
+
+fig_giraffe = plot.blind.explain_differences(database, blind_giraffe,
+    __comparison_filename="ges-dr5-giraffe-blind-test-comparison.fits",
+    group_by=("wg", "name"))
+fig_giraffe.savefig("figures/blind-test/ges-dr5-giraffe-blind-test-explaination.pdf", dpi=150)
+fig_giraffe.savefig("figures/blind-test/ges-dr5-giraffe-blind-test-explaination.png", dpi=150)
+
+
+fig_giraffe, comparison_giraffe = plot.blind.differences_wrt_snr(
+    database, benchmarks, blind_giraffe,
[…]

### 2017-02-06 scripts/ship_wg10.py

@@ -1,0 +1,36 @@
+
+"""
+Ship a WG10 recommended SP product.
+"""
+
+import yaml
+import logging
+
+from code import GESDatabase, ship
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+
+# Produce a PER-SETUP file even though they will be duplicates.
+ship.wg_recommended_sp_template(database,
+    "fits-templates/recommended-templates/GES_iDR5_WG10_RecommendedTemplate_14072016_PERSETUP_FixedLengthFLAGColumns.fits",
+    "outputs/GES_iDR5_WG10_Recommended_PERSETUP.fits",
+    10, overwrite=True, match_by_setup=True)
+
+
+raise a
+
+# Produce a per CNAME file.
+ship.wg_recommended_sp_template(database,
+    "fits-templates/recommended-templates/GES_iDR5_WG11_RecommendedTemplate_16072016_FixedLengthFLAGColumns.fits",
+    "outputs/GES_iDR5_WG11_Recommended.fits",
+    11, overwrite=True)
+
+

### 2017-02-06 scripts/test_wg10_combinations.py

@@ -1,0 +1,114 @@
+
+"""
+Test different mappings between WG10 nodes.
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase
+from code.model.combined import CombinedModel
+
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+
+# Only use "benchmarks" with TEFF < 8000 K
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+benchmarks["E_FEH"] = 0.10
+
+vector_terms = {
+    "teff":[
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+        (("teff", "logg", ), 1),
+        (("teff", "feh", ), 1),
+        (("logg", "feh", ), 1),
+        (("teff", ), 2),
+        (("logg", ), 2),
+        (("feh", ), 2),
+    ],
+    "logg": [
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+        (("teff", "logg", ), 1),
+        (("teff", "feh", ), 1),
+        (("logg", "feh", ), 1),
+        (("teff", ), 2),
+        (("logg", ), 2),
+        (("feh", ), 2)
+    ],
+    "feh": [
+        (("feh", ), 1),
+    ]
+
+}
+
+
+models = {}
+for parameter in ("teff", "logg", "feh"):
+
+
+    model = CombinedModel(database, 10, parameter, benchmarks)
+
+    data, metadata = model._prepare_mapped_data(
+        vector_terms=vector_terms[parameter],
+        reference_node_id=database.retrieve_node_id(10, "Lumba-HR10|HR21"),
+        minimum_node_estimates=3,
+        sql_constraint_for_mapping_query=\
+            "r.snr > 10 and r.teff > 4000 and r.teff < 6250 and "
+            "r.logg > 0 and r.logg < 5 and r.feh > -1.5 and r.feh < +0.25"
+            " and passed_quality_control",
+        sql_constraint_for_data_query=None)
+
[…]

### 2017-02-07 code/model/combined.py
trying to map to maxplanck now

@@ -378,7 +378,7 @@ class CombinedModel(BaseCombinedModel):
         # Get the node data for all the benchmarks.
         data = self._database.retrieve_table(
             """ WITH    n AS (
-                            SELECT id FROM nodes WHERE wg = {wg}), 
+                            SELECT id, name FROM nodes WHERE wg = {wg}), 
                         s AS (
                             SELECT cname, ges_type, ges_fld
                             FROM spectra
@@ -456,6 +456,13 @@ class CombinedModel(BaseCombinedModel):
             y[node_id] = np.array(y[node_id])
             before[node_id] = np.array(before[node_id])
 
+            finite = np.isfinite(y[node_id]) * np.all(np.isfinite(x[node_id]), axis=0)
+            
+            x[node_id] = x[node_id][:, finite]
+            y[node_id] = y[node_id][finite]
+            before[node_id] = before[node_id][finite]
+
+
         # For each node, find the coefficients to map the results.
         model = lambda x, *theta: np.dot(theta, x)
 
@@ -464,6 +471,7 @@ class CombinedModel(BaseCombinedModel):
         for node_id in set(data["node_id"]):
 
             xn, yn = (x[node_id], y[node_id])
+
             theta, cov = op.curve_fit(model, xn, yn, p0=np.zeros(xn.shape[0]))
             
             mapping_coefficients[node_id] = (theta, cov)

### 2017-02-07 sandbox_plot_wg_clusters.py

@@ -92,5 +92,5 @@ fig = plot.hertzsprung_russell_diagrams(database, figsize=(10.725, 12.4125),
     cluster_names=cluster_names, velocity_constraints=velocity_constraints,
     metallicity_constraints=metallicity_constraints, wgs=(10, 11, ),
     isochrone_filenames=isochrone_filenames,
-    sql_constraint="(r.wg = 10 and trim(r.setup) = 'HR10|HR21' and r.snr > 10 and r.nn_nodes_teff > 1) or (r.wg = 11 and r.nn_nodes_teff > 5)")#="((s.wg = 110 and r.nn_nodes_teff > 1 and r.snr > 10 and r.teff > 4000 and r.teff < 6500) or (s.wg != 110 and s.wg != 11) or (s.wg = 11 and r.nn_nodes_teff > 2))")
+    sql_constraint="(r.wg = 10 and trim(r.setup) = 'HR10|HR21' and r.snr > 10 and r.nn_nodes_teff > 1) or (r.wg = 11 and r.nn_nodes_teff > 1 and r.snr > 10)")#="((s.wg = 110 and r.nn_nodes_teff > 1 and r.snr > 10 and r.teff > 4000 and r.teff < 6500) or (s.wg != 110 and s.wg != 11) or (s.wg = 11 and r.nn_nodes_teff > 2))")
 fig.savefig("figures/ges-dr5-clusters-all-wgs-hrds-20170206.pdf", dpi=300)

### 2017-02-07 sandbox_plot_wg_performance.py

@@ -27,9 +27,28 @@ debug = True
 cluster_velocities = Table.read("fits-templates/oc_gc_radial_vel.dat", format="ascii")
 
 
-for wg in (10, ):
+for wg in (11, ):
 
-    sql_constraint = "TRIM(r.SETUP) = 'HR10|HR21'"
+    sql_constraint = None # "TRIM(r.SETUP) = 'HR10|HR21'"
+
+    # Plot benchmarks first.
+    fig = plot.wg_benchmark_performance(database, wg, benchmarks, 
+        show_recommended=True, ylims=dict(TEFF=1000, LOGG=1, FEH=1),
+        recommended_sql_constraint=None, #"TRIM(wgr.SETUP) = 'HR10|HR21'",
+        recommended_table="wg_recommended_results")
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.pdf".format(wg=wg), **savefig_kwds)
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.png".format(wg=wg), **savefig_kwds)
+
+
+    fig = plot.wg_benchmark_performance(
+        database, wg, benchmarks, show_recommended=True,
+        recommended_sql_constraint=None, #"TRIM(wgr.SETUP) = 'HR10|HR21'",
+        recommended_table="wg_recommended_results")
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks.pdf".format(wg=wg), **savefig_kwds)
+    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks.png".format(wg=wg), **savefig_kwds)
+
+
+    raise a
 
 
     for isochrone in isochrones:
@@ -91,22 +110,6 @@ for wg in (10, ):
                 print("Created figure {}.pdf".format(basename))
 
 
-
-    # Plot benchmarks first.
-    fig = plot.wg_benchmark_performance(database, wg, benchmarks, 
-        show_recommended=True, ylims=dict(TEFF=1000, LOGG=1, FEH=1),
-        recommended_sql_constraint="TRIM(wgr.SETUP) = 'HR10|HR21'",
-        recommended_table="wg_recommended_results")
-    fig.savefig("figures/wg{wg}/wg{wg}-benchmarks-zoom.pdf".format(wg=wg), **savefig_kwds)
[…]

### 2017-02-07 sandbox_plotting.py

@@ -29,7 +29,7 @@ database = GESDatabase(**credentials)
 
 
 debug = False
-wgs = (10, )#11, 12, 13)
+wgs = (11, )#11, 12, 13)
 parameters = ("teff", "logg", "mh", "xi")
 isochrones = glob("isochrones/*.dat")
 

### 2017-02-07 scripts/homogenise_combined_wg10_wrt_mp.py

@@ -39,10 +39,30 @@ model_paths = "homogenisation-wg{wg}-{parameter}-{setup}-combined-wrt-MaxPlanck.
 
 wgs = (10, )
 parameter_scales = OrderedDict([
-    ("teff", 250),
-    ("logg", 0.25),
+#    ("teff", 250),
+#    ("logg", 0.25),
     ("feh", 0.25)
 ])
+
+
+vector_terms = {
+    "teff":[
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+    ],
+    "logg": [
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+    ],
+    "feh": [
+        (("feh", ), 1),
+    ]
+
+}
+
+reference_node_id = database.retrieve_node_id(10, "MaxPlanck-HR21")
 
 
 sample_kwds = dict(chains=2, iter=4000)
@@ -62,12 +82,18 @@ for wg in wgs:
                 model = CombinedModel.read(model_path, database)
                 
             else:
-                model = CombinedModel(database, wg, parameter, benchmarks)
-
-                data, metadata = model._prepare_data(
+                model = CombinedModel(database, 10, parameter, benchmarks)
+                data, metadata = model._prepare_mapped_data(
                     default_sigma_calibrator=default_sigma_calibrator, 
                     minimum_node_estimates=1,
-                    sql_constraint="TRIM(name) LIKE '%-{}'".format(setup))
+                    vector_terms=vector_terms[parameter],
+                    reference_node_id=reference_node_id,
+                    sql_constraint_for_mapping_query="(r.teff < 6000 or name not like 'Nice%') and r.snr > 50 and r.teff > 4000 and r.teff < 6500 and "
+                        "r.logg > 0 and r.logg < 5 and r.feh > -1 and r.feh < +0.25"
+                        " and passed_quality_control and (trim(name) like '%-{setup}' or node_id = {reference_node_id})".format(
+                            setup=setup, reference_node_id=reference_node_id),
+                    sql_constraint_for_data_query="TRIM(name) LIKE '%-{}'".format(setup),
+                    match_by="cname")
 
 
                 init = {
@@ -87,7 +113,6 @@ for wg in wgs:
                 model.write(model_path, 
                     overwrite=True, __ignore_model_pars=("Sigma", "full_rank_estimates"))
 
-
[…]

### 2017-02-07 scripts/ingest_recommended.py

@@ -25,6 +25,7 @@ database = GESDatabase(**credentials)
 
 # Ingest results 
 filenames = glob("recommended-results/GES_iDR5_WG??_Recommended.fits")
+filenames = ["recommended-results/GES_iDR5_WG13_Recommended_PERSETUP.fits"]
 for filename in filenames:
     logger.info("Ingesting from {}".format(filename))
     database.ingest_recommended_results(filename, extension=1)

### 2017-02-07 scripts/map_wg10_nodes_to_bms.py

@@ -1,0 +1,191 @@
+
+"""
+Test different mappings between WG10 nodes.
+"""
+
+import yaml
+import logging
+import numpy as np
+import os
+from astropy.table import Table
+from collections import OrderedDict
+
+
+from code import GESDatabase
+from code.model.combined import CombinedModel
+
+
+# Initialize logging.
+logger = logging.getLogger("ges")
+
+# Create a database object.
+db_filename = "db.yaml"
+with open(db_filename, "r") as fp:
+    credentials = yaml.load(fp)
+database = GESDatabase(**credentials)
+
+
+# Assign the nodes new names first.
+old_nodes = database.retrieve_table("""
+    SELECT DISTINCT ON (nodes.name, setup) nodes.id, nodes.name, setup
+    FROM results, nodes
+    WHERE results.node_id = nodes.id
+      AND nodes.wg = 10
+      AND results.teff <> 'NaN'""")
+
+for old_node in old_nodes:
+
+    if "-" in old_node["name"]:
+        print("Skipping {}".format(old_node["name"]))
+        continue
+
+    new_node_name = "{name}-{setup}".format(
+        name=old_node["name"], setup=old_node["setup"].strip())
+
+    new_node_id = database.create_or_retrieve_node_id(10, new_node_name)
+
+    N = database.update("""
+        UPDATE results 
+        SET node_id = %s
+        WHERE node_id = %s
+          AND TRIM(setup) = %s;
+        """, (new_node_id, old_node["id"], old_node["setup"].strip()))
+
+    print(old_node["id"], old_node["name"], old_node["setup"].strip(), new_node_id, new_node_name, N)
+
+database.connection.commit()
+
+# Only use "benchmarks" with TEFF < 8000 K
+benchmarks = Table.read("fits-templates/benchmarks/GES_iDR5_FGKM_Benchmarks_ARC_29092016.fits")
+benchmarks = benchmarks[benchmarks["TEFF"] < 8000]
+benchmarks["E_FEH"] = 0.10
+
+vector_terms = {
+    "teff":[
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+    ],
+    "logg": [
+        (("teff", ), 1),
+        (("logg", ), 1),
+        (("feh", ), 1),
+    ],
+    "feh": [
+        (("feh", ), 1),
+    ]
+
+}
+
[…]

### 2017-02-07 scripts/ship_wg11.py

@@ -24,6 +24,8 @@ ship.wg_recommended_sp_template(database,
     "outputs/GES_iDR5_WG11_Recommended_PERSETUP.fits",
     11, overwrite=True)
 
+raise a
+
 # Produce a per CNAME file.
 ship.wg_recommended_sp_template(database,
     "fits-templates/recommended-templates/GES_iDR5_WG11_RecommendedTemplate_16072016_FixedLengthFLAGColumns.fits",
